---
title: "Institution Report: SWiMS 2024 Data"
subtitle: "Institution: `r levels(dat$institution)[params$object.inst]`"
author: "a project by"
# date: "`r Sys.Date()`"
params:
  object.inst: 2
  font_text: 20
  font_anno: 10
  fontsize_inplot_text: 9
  cut_off: 10
  del_small_groups: FALSE
  alpha_val: 0.4
  bar_width: 0.8
output:
  pdf_document:
    toc: false
    toc_depth: 3
    keep_tex: true
    fig_caption: false
    latex_engine: xelatex   # or lualatex
bibliography: references.bib 
classoption: landscape
geometry: top=1.5cm, bottom=1.2cm, left=1cm, right=1cm
header-includes:
  - \usepackage{graphicx}
  - \usepackage{fancyhdr}
  - \usepackage{hyperref}
  - \usepackage{float}
  - \usepackage{fontspec}
  - \setmainfont{blue_highway_rg.otf}[ Path = ../data/Fonts/, BoldFont = Blue_Highway_Bd.otf]
  - \usepackage{xcolor}
  - \pagestyle{fancy}
  - \fancyhead[L]{\includegraphics[width=2.5cm]{../data/actionuni_MAIN_LOGO_RVB.jpg}}
  #- \fancyhead[L]{\includegraphics[width=1.5cm]{actionuni_logo_klein.png}}
  - \fancyhead[C]{}
  - \fancyhead[R]{SWiMS 2024 `r levels(dat$institution)[params$object.inst]` Report}
  - \hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue,pdfborder={0 0 1}}
  - \usepackage{titling}
  - \usepackage{draftwatermark}
  - \SetWatermarkText{DRAFT}
  - \SetWatermarkScale{1}
  - \SetWatermarkLightness{0.9}
  - \usepackage{titling}
  - |
    \preauthor{\begin{center}}
    \postauthor{\par\vspace{1em}\href{https://actionuni.ch/}{\includegraphics[width=8cm]{../data/actionuni_EN_LOGO_DEF_RVB.jpeg}}\\
    \href{https://actionuni.ch/}{actionuni.ch}\end{center}}
  - \usepackage{eso-pic}
  - |
    % ---- Title-page bottom-right image, first page only ----
    \AddToShipoutPicture*{%
      \put(\LenToUnit{\paperwidth-2cm},\LenToUnit{1cm}){%
        \makebox(0,0)[rb]{%
          \includegraphics[width=0.5\paperwidth,keepaspectratio]{../data/actionuni_frontpage.jpeg}%
        }%
      }%
    }
  - |
    % ---- Title-page left-side text, first page only ----
    \newcommand\TitlePageText{%
      \put(\LenToUnit{2cm},\LenToUnit{11cm}){%  % moved 4cm up
        \parbox[t][0.6\textheight][t]{0.7\textwidth}{%
          Key Takeaways:
          \begin{itemize}

          \end{itemize}
        }%
      }%
    }
    \AddToShipoutPicture*{\TitlePageText}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = FALSE, message = FALSE,
                      out.width = "70%",
                      fig.width = 16,        
                      fig.height = 14,   
                      fig.align = 'center', 
                      fig.pos = 'H',
                      dpi = 300)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(readxl)
library(dplyr)
```

```{r load-data, include=FALSE}
# Load data
load("../data/SWiMS2024_Data_2025-09-08.RData") 
source("zz_utils_helpers.R")
source("zz_utils_distribution.R")
source("zz_utils_aggregation.R")
source("zz_utils_multibar.R")

target_institution <- levels(dat$institution)[params$object.inst]
```

\newpage 
\setcounter{tocdepth}{2}
\tableofcontents
\vfill  
**CRediT (Contribution Roles Taxonomy) author statement:** 

**Zoran Kovacevic\*, Neele H. Heiser\*, Patricia Eiche\* , Timon Elmer\* **: Conceptualization; Methodology; Validation; Investigation; Supervision; Project administration 

**Zoran Kovacevic\*, Timon Elmer\* **: Formal analysis; Data Curation; Visualization

\* shared first-authorship

\textit{Version 1.0 — `r Sys.Date()`}  

\newpage

# Introduction

The Swiss-Wide Mental Health Survey (SWiMS) 2024 explores the mental health and well-being of Swiss academic mid-level staff, including doctoral researchers, postdoctoral researchers, and other non-faculty academic staff. The survey aims to identify key challenges in working conditions and research environments, providing a data-driven foundation for improving policies and support systems at Swiss higher education institutions.

This report presents the findings of the institution **`r target_institution`**, offering descriptive data into mental health outcomes, stressors, available resources, sources of discrimination, and questionable research practices. The responses of the specific institution are compared to all other part-taking institutions combined (see Chapter: Partaking institutions and response counts). 

### Background and motivation
Academic mid-level staff are essential to research, teaching, and student supervision, making up approximately 48% of the academic workforce in Switzerland (Federal Statistical Office, 2024). The mid-level faculty thus makes a decisive contribution to the innovative strength and competitiveness of the university system as well as to the quality of teaching and training.  
Despite their central role, academic mid-level staff are often exposed to a variety of stresses. The work pressure is high due to the demands of research, teaching and administrative tasks [@barkhuizen2014; @mattijssen2020]. Added to this is the increasing pressure to publish, reinforced by the “publish or perish” principle, which has a significant influence on academic careers [@miller2011; @tijdink2013]. Many early career researchers also struggle with the uncertainty of their professional future, as most positions are temporary and the prospect of a long-term academic career is very limited [@petersen2012; @nagy2019; @guidetti2022].

These factors in the academic environment can have a negative impact on the mental health of early career researchers [@bolotnyy2022; @urbina2020]. International studies show that 30–40% of researchers suffer from mental health problems [@divaris2012; @gloria2016; @levecque2017; @evans2018; @mattijssen2020; @estupina2024]. Other international studies also document high rates of burnout (9%), depression (17–24%) and anxiety (17%) among early career researchers [@bolotnyy2022; @boone2022; @evans2018; @satinsky2021]. In the long term, this jeopardizes the quality of research and the innovative strength of universities [@amer2022; @barry2018].


Despite growing awareness of these issues inernationally, Switzerland lacks comprehensive national data on the mental health of academic mid-level staff. While some institutions have conducted internal surveys (e.g., [ETH Zurich’s employee survey](https://vseth.ethz.ch/politik/wiegeths/)), a coordinated, nationwide effort has been missing that allows identification of national and local areas of improvement. The last nationwide report on the working conditions of Swiss mid-level staff was conducted -- also by actionuni -- in 2009 (see SBFI report [here](https://www.sbfi.admin.ch/sbfi/en/home/services/publications/data-base-publications/study-research-and-teaching-assistants.html)).

### The Swiss-Wide Mental Health Survey (SWiMS)

To address this gap, actionuni, in collaboration with 13 academic mid-level staff associations, launched SWiMS 2024 as a bottom-up initiative. The survey was developed jointly by the actionuni survey team and representatives of academic mid-level staff associations, and formally approved at the actionuni General Assembly in late 2023. The survey provides a nationwide assessment of mental health among academic mid-level staff in Switzerland, highlighting both stressors and protective factors.

<!-- By systematically analyzing the collected data, the project aims to: -->

<!-- - Expand the knowledge base on mental health in academia. -->
<!-- - Identify key stress factors affecting mid-level academic staff. -->
<!-- - Enable institutions to learn from best practices, improving support systems. -->
<!-- - Provide an evidence-based foundation for discussions on mental health policies. -->

<!-- Ultimately, fostering a healthier academic work environment benefits not only early career researchers but also research quality, institutional innovation, and the broader university system. Ensuring well-being at all career stages is essential for maintaining the long-term excellence and sustainability of Swiss academia. -->


Participation in the survey was entirely anonymous and voluntary, and respondents could withdraw at any time during the process. Ethical approval was obtained from the ethics Committee of the Faculty of Philosophy of the University of Zurich (nr. 23.12.07). Data was collected between May 13th and October 31st 2024. The survey was presented to participants in English.

### Anonymisation
To prevent potential re-identification and protect individual privacy, any demographic categories with fewer than 10 data points were excluded from the analysis. This measure ensures that no specific demographic group can be linked back to a particular individual, thereby upholding the anonymity and confidentiality of the participants. This exclusion criterion was applied exclusively to demographic categories in the relation to other variables in the dataset.

### Sharing of raw data

As resources for preparing the data for open access are currently unavailable, it is possible that a public release of anonymized raw data may not take place. For this reason, the present report provides a detailed overview of the findings -- spanning more than 200 pages -- to provide broad accessibility of the results.

# Partaking Institutions

### Data cleaning 

Only institutions with more than 10 responses were considered in this report. 43 participants of 16 institution with a mean of 2.7 (SD = 1.81) participants were removed from the dataset. 62 additional responses were removed because institution "Other" (n = 44), "Prefer not to say" (n = 15), or were missing (n = 3) were indicated. We also excluded participants that took shorter than 4 minutes to respond (n = 4). In total, `r nrow(dat)` responses were part of this report. Responses numbers in the different plots may vary due to missing responses on a particular question or on grouping variables (e.g., age category).


### Partaking institutions and response counts

```{r, echo = F, fig.width = 8, fig.height = 4.5}

# Calculate the number of participants for each institution
institution_counts <- dat %>%
  group_by(inst) %>%
  summarise(count = n()) %>%
  filter(count > 10)

# Filter the data to include only institutions with more than 20 participants
filtered_dat <- dat %>%
  filter(inst %in% institution_counts$inst)

# Get the maximum count to set y-axis limit
max_count <- max(institution_counts$count)
sum_count <- sum(institution_counts$count)

# Create the plot
ggplot(filtered_dat, aes(x = reorder(factor(inst), table(inst)[factor(inst)]), y = ..count..)) +  
  geom_bar(fill = cols_categorical[1]) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.caption = element_text(size = 8, hjust = 0.5, face = "italic")
  ) +
  labs(
    # title = "Number of Responses by Institution",
    x = "Institution Name",
    y = "Number of Responses",
    caption = paste("Total count: ",sum_count ,"\n",
                    "Only institutions with more than 10 participants are displayed.")
  ) +
  geom_text(stat = 'count', aes(label = ..count..), hjust = -0.1, size = 3.5) +
  ylim(c(0, max_count + 30)) +
  coord_flip()

#ggsave(paste0("../plots/SWiMS_responses_",date ,".pdf"), height = 7, width = 8)
```

The average duration of responding to the survey was `r round(mean(dat[dat$duration < 2*3600,"duration"]/60, na.rm =T),2)` minutes (SD = `r round(sd(dat[dat$duration < 2*3600,"duration"]/60, na.rm =T),2)`).


# How to read the key plots

### Distribution plots
```{r, echo=FALSE, fig.align='center', out.width='100%'}
knitr::include_graphics("../data/howtoread_plot1.pdf")
```
\newpage

### Grouped questions plots
```{r, echo=FALSE, fig.align='center', out.width='100%'}
knitr::include_graphics("../data/howtoread_plot2.pdf")
```
\newpage

# Sample Description

## Response Rate

```{r}

institution_counts <- dat %>%
  group_by(inst) %>%
  summarise(count = n()) %>%
  filter(count > 10)

institution_counts <- institution_counts %>%
  left_join(dat.meta %>% select(Name, Members), by = c("inst" = "Name")) # add member numbers
institution_counts$response_rate <- institution_counts$count/institution_counts$Members



```

`r institution_counts[institution_counts$inst %in% target_institution,"count"]` responses were collected from `r target_institution` with a total number of members estimated at `r institution_counts[institution_counts$inst %in% target_institution,"Members"]` (taken from the actionuni reports on memberships), corresponding to a participation rate of `r round(institution_counts[institution_counts$inst %in% target_institution,"response_rate"]*100,1)`%.


## Demographics

The figures below summarize the key demographic characteristics of the specific institution compared to all remaining partaking institutions.

### Age
```{r age}
swims.plot.distribution("age",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups,
                        width_bar = params$bar_width)

```
\normalsize
`r swims.formulation("age")`
For the subsequent analyses this variable was grouped into three categories: "18-30", "31-40", and ">41". Respondents unwilling to disclose their age were coded as missing.
\normalsize

\newpage
### Gender

```{r gender}
swims.plot.distribution("Gender",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```

\normalsize
`r swims.formulation("genderNA")`
Recoded from multiple binary selections into categories: "male," "female," or "other" (including nonbinary or multiple selections). "Prefer not to say" responses were coded as missing (NA).
\normalsize

\newpage
### Research Discipline

```{r }
swims.plot.distribution("researchDiscipline",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("researchDiscipline")`
Subsequently referred to as "Natural Sciences and Engineering", "Medicine", "Social Sciences", and "Humanities". "Prefer not to say" responses coded as NA.
\normalsize

\newpage
### Position Type

```{r }
swims.plot.distribution("mainPosition",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups,
                        width_text = 25)
```
\normalsize
`r swims.formulation("mainPosition")`
Recoded positions into four broad groups: "Researcher aiming for a PhD,", "Postdoctoral researcher", "Other researchers with a PhD", and "Other". "Prefer not to say" responses coded as NA. The group "Other researchers with a PhD" consisted of categories "Researcher above postdoc (habilitated or equivalent)", "Other researchers with a PhD". The group "Other" consisted of categories "Supportive positions (e.g., administrative personnel, technical staff)" and "Lecturing only".

\normalsize

\newpage
### Funding source

```{r }
 swims.plot.distribution("funding",
                         institution_prov = target_institution,
                         font_size = params$font_text,
                         annoFontSize = (params$font_anno - 3),
                         cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("funding")`
Original funding categories simplified into three groups: "SNSF", "Non-SNSF funding", and "University/Higher education institute." Ambiguous or undisclosed funding sources coded as missing (NA).
\normalsize

\newpage
### Residence status

```{r }
swims.plot.distribution("residenceStatus",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("residenceStatus")`
Subsequently used with residence status reduced to two groups: "Swiss citizenship + Permit C", and "Other Permits." Non-disclosed or unclear responses coded as NA.
\normalsize

\newpage
### Care work

```{r}
swims.plot.distribution("Carework",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("careFamily")`
`r swims.formulation("careKids")`
Simplified into "care work" (if respondents indicated caring for children/family) or "no care work". Missing or unclear responses were coded as missing.
\normalsize

\newpage
### Other demographic variables

These variables will not be used for group comparisons later, thus the name "other".


#### Employment Status

```{r }
swims.plot.distribution("employmentStatus",
                          institution_prov = target_institution,
                          font_size = params$font_text,
                          annoFontSize = (params$font_anno - 3),
                          cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                          small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
`r swims.formulation("employmentStatus", what = "item")`
\normalsize

\newpage
#### Employment Percentage

```{r}
swims.plot.distribution("workloadMainjob",
                          institution_prov = target_institution,
                          font_size = params$font_text,
                          annoFontSize = (params$font_anno - 3),
                          cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                          small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("employmentStatus", what = "item")`
\normalsize

\newpage
#### Additional Non-Academic Job

```{r}
swims.plot.distribution("nonacademicJob",
                          institution_prov = target_institution,
                          font_size = params$font_text,
                          annoFontSize = (params$font_anno - 3),
                          cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                          small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("nonacademicJob", what = "item")`
\normalsize

\newpage
# Mental Health
## General Mental Health
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize
```{r, out.width = "65%"}
swims.plot.distribution("mentalHealth",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```

\newpage
### General Mental Health by Age
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize

```{r}
swims.plot.distribution("mentalHealth",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### General Mental Health by Gender
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize

```{r}
swims.plot.distribution("mentalHealth",
                         institution_prov = target_institution,
                         divider = "Gender",
                         font_size = params$font_text,
                         annoFontSize = (params$font_anno - 3),
                         cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### General Mental Health by Research Discipline
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize

```{r}
swims.plot.distribution("mentalHealth",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### General Mental Health by Position Type
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize

```{r}
swims.plot.distribution("mentalHealth",
                         institution_prov = target_institution,
                         divider = "Position",
                         font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                         cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### General Mental Health by Care Work
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize

```{r}
swims.plot.distribution("mentalHealth",
                         institution_prov = target_institution,
                         divider = "Carework",
                         font_size = params$font_text,
                         annoFontSize = (params$font_anno - 3),
                         cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### General Mental Health by Funding Source
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize

```{r}
swims.plot.distribution("mentalHealth",
                         institution_prov = target_institution,
                         divider = "Funding",
                         font_size = params$font_text,
                         annoFontSize = (params$font_anno - 3),
                         cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Depression

```{r}
library(psych)

side_obj <- dat %>%
  filter(inst == target_institution) %>%
  select(paste0("depression_", c(1:7)))

del <- which(!complete.cases(side_obj))

if(length(del) > 0) {
  side_obj <- side_obj[-del, ]
}

cronbach <- alpha(side_obj)

```

We computed a depression score by summing the 7 items from the DASS-21 depression subscale. In our sample, this measure showed internal consistency of Cronbach’s alpha = `r round(cronbach$total[2],2)`. A total of `r length(del)` observations were excluded from this analysis due to missing data on at least one of the depression items.
**Following the clinical guidelines proposed by Nilges and Essau [-@nilges_dass_2021], a sum score above 10 is considered indicative of elevated depressive symptoms and may be viewed as clinically relevant**.

```{r}
swims.plot.distribution("Depression",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = (params$bar_width - 0.5),
                        small.group.delete = params$del_small_groups,
                        fct_ord = c(0:21))

swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Depression by Age

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Gender

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Research Discipline

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Position Type

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Care Work

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Funding Source

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Burnout
\normalsize
`r swims.formulation("Burnout", what = "item")`

Item developed by West and colleauges [-@west_single_2009].
\normalsize

```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Burnout by Age
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize

```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Gender
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize

```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Research Discipline
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize

```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Position Type
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize

```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Care Work
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize

```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Funding Source
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize

```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Awareness Resources

```{r, out.width = "65%"}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    alpha_plot = params$alpha_val)
```

\newpage
### Awareness Resources by Age

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awareness Resources by Gender

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awareness Resources by Research Discipline

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awareness Resources by Position Type

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awareness Resources by Care Work

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awareness Resources by Funding Source

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Job Satisfaction
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`

Item developed by Dolbier and colleauges [-@dolbier_reliability_2005].
\normalsize

```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Job Satisfaction by Age
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize

```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Gender
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize

```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Research Discipline
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize

```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Position Type
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize

```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Care Work
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize

```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Carework",
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Funding Source
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize

```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Quitting Intentions by Age
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Gender
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Research Discipline
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Position Type
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Care Work
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Funding Source
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize

```{r}
swims.plot.distribution("stress",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Stress by Age
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Gender
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Research Discipline
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Position Type
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Care Work
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Funding Source
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize

```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Stressors
## System Stressors
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    rev_colors_set = TRUE)
```
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```

\newpage
### System Stressors by Age
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Gender
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\newpage
\normalsize
`r imp_mess`
\normalsize
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Research Discipline
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Position Type
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Care Work
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Funding Source
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Supervisor Stressors
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Supervisor Stressors by Age
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Gender
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Research Discipline
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Position Type
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Care Work
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Funding Source
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Colleagues Stressors
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Colleagues Stressors by Age
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Gender
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Research Discipline
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Position Type
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Care Work
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Funding Source
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Self-Management Stressors
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    rev_colors_set = TRUE,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Self-Management Stressors by Age
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Gender
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Research Discipline
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Position Type
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Care Work
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Funding Source
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Private Stressors
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Private Stressors by Age
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Gender
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Research Discipline
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Position Type
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Care Work
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize

```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Funding Source
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Statements Regarding Supervisor
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Supervisor by Age
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Gender
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Research Discipline
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Position Type
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Care Work
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Funding Source
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Statements Regarding Institution
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Institution by Age
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Gender
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Research Discipline
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Position Type
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Care Work
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Funding Source
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Statements Regarding Work-Group
These workgroup-related questions were asked only if the respondents indicated to be in a working group.

\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Work-Group by Age
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Gender
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Research Discipline
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Position Type
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Care Work
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Funding Source
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize

```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Discrimination
## Discrimination Experience
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r, out.width = "65%"}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Discrimination Experience by Age
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Gender
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Research Discipline
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Position Type
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Care Work
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Funding Source
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize

```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    rev_colors_set = TRUE,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Sources of Discrimination
\normalsize
`r swims.formulation("discrAge", what = "item")`
\normalsize

```{r}
swims.plot.aggregation("discrimination_type",
                       institution_prov = target_institution,
                       font_size = params$font_text,
                       colors_set = "Set1"
                       )
```

<!-- \newpage -->
<!-- ## Amount of Sources of Discrimination -->
<!-- \normalsize -->
<!-- `r swims.formulation("discrAge", what = "item")` -->
<!-- \normalsize -->

<!-- ```{r} -->
<!-- swims.plot.aggregation("discrimination_type", -->
<!--                        institution_prov = target_institution, -->
<!--                        font_size = (params$font_text + 5), -->
<!--                        count_votes_at_all = TRUE) -->
<!-- ``` -->

\newpage
## Reporting Information
\normalsize
`r swims.formulation("discrReport", what = "item")`
\normalsize

```{r}
swims.plot.distribution("discrReport",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```

\newpage
# Questionable Research Practices
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
qrp.cols <- c("red","#66C2A5","gray69","orange","#2166AC")
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Questionable Research Practices by Age
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Questionable Research Practices by Gender
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Questionable Research Practices by Research Discipline
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Questionable Research Practices by Position Type
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Questionable Research Practices by Care Work
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Questionable Research Practices by Funding Source
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize

```{r, out.width = "70%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    fill_color_set = qrp.cols
                    )
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Pressures to Perform Questionable Research Practices
\normalsize
`r swims.formulation("pressureqrpFunder", what = "item")`
\normalsize

```{r}
swims.plot.aggregation("qrp_pressure",
                       institution_prov = target_institution,
                       font_size = params$font_text,
                       colors_set = "Set1")
```

\newpage
## Effects of Pressures to Perform Questionable Research Practices on Mental Health
\normalsize
`r swims.formulation("pressureqrpMentalhealth", what = "item")`
\normalsize

```{r}
swims.plot.distribution("pressureqrpMentalhealth",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = (params$font_anno - 3),
                        cut.small.groups = params$cut_off,
                        width_bar = params$bar_width,
                        small.group.delete = params$del_small_groups)
```

\newpage
# Appendix

## Detailed survey content and codebook

Detailed item formulations, variables, etc. can be found in the codebook and survey-PDF on the [OSF repository of this project: https://osf.io/kqdnm](https://osf.io/kqdnm).


# References


