---
title: "Institution Report: SWiMS 2024 Data"
author: "actionuni Survey Team"
date: "`r Sys.Date()`"
params:
  object.inst: 5
  font_text: 16
  font_anno: 6
  fontsize_inplot_text: 10
  cut_off: 10
  del_small_groups: FALSE
  alpha_val: 0.4
output:
  pdf_document:
    toc: true
    toc_depth: 3
    keep_tex: true
    fig_caption: false
bibliography: references.bib 
classoption: landscape
geometry: top=1.5cm, bottom=1.5cm, left=1cm, right=1cm
header-includes:
  - \usepackage{graphicx}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  #- \fancyhead[L]{\includegraphics[width=1.5cm]{actionuni_logo_klein.png}}
  - \fancyhead[C]{}
  - \fancyhead[R]{SWiMS 2024 Institution Report}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = FALSE, message = FALSE,
                      out.width = "70%",
                      fig.width = 16,        
                      fig.height = 14,   
                      fig.align = 'center', 
                      fig.pos = 'H',
                      dpi = 300)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(readxl)
library(dplyr)
```

```{r load-data, include=FALSE}
# Load data
load("../data/SWiMS2024_Data_2025-03-29.RData") # ToDo: wir müssen unbedingt drauf achten dass alles nutzbar ist für beide ich kann data cleaningn icht nutzen weil mir ien objekt fehlt
source("zz_utils_helpers.R")
source("zz_utils_distribution.R")
source("zz_utils_aggregation.R")
source("zz_utils_multibar.R")

target_institution <- levels(dat$institution)[params$object.inst]
```

# Introduction

The **SWiMS 2024 Survey** explores the mental health and well-being of mid-level academic staff (e.g., doctoral researchers, scientific associates, postdocs, and other scientific staff) in Switzerland. The goal is to identify problems and areas for improvement in working conditions and research environments. This report focuses on the institution **`r target_institution`**, comparing its responses to those from other institutions.

---
  
# Sample Description

## Response Rate

```{r}

institution_counts <- dat %>%
  group_by(inst) %>%
  summarise(count = n()) %>%
  filter(count > 10)

institution_counts <- institution_counts %>%
  left_join(dat.meta %>% select(Name, Members), by = c("inst" = "Name")) # add member numbers
institution_counts$response_rate <- institution_counts$count/institution_counts$Members



```

`r institution_counts[institution_counts$inst %in% target_institution,"count"]` responses were collected from `r target_institution` with a total number of members estimated at `r institution_counts[institution_counts$inst %in% target_institution,"Members"]` (taken from the actionuni reports on memberships), corresponding to a participation rate of `r round(institution_counts[institution_counts$inst %in% target_institution,"response_rate"]*100,1)`%.


## Demographics

The figures below summarize the key demographic characteristics of all parttaking institutions.

### Age

```{r age}
swims.plot.distribution("age",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("age")`  
For the subsequent analyses this variable was grouped into three categories: "18-30", "31-40", and ">41". Respondents unwilling to disclose their age were coded as missing.
\normalsize

\newpage
### Gender

```{r gender}
swims.plot.distribution("Gender",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```

\normalsize
`r swims.formulation("female")`  
`r swims.formulation("male")`  
`r swims.formulation("nonbinary")`  
`r swims.formulation("genderNA")`  
Recoded from multiple binary selections into categories: "male," "female," or "other" (including nonbinary or multiple selections). "Prefer not to say" responses were coded as missing (NA).
\normalsize

\newpage
### Research Discipline

```{r }
swims.plot.distribution("Discipline",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("researchDiscipline")`  
Subsequently referred to as "Natural Sciences and Engineering", "Medicine", "Social Sciences", and "Humanities". "Prefer not to say" responses coded as NA.
\normalsize

\newpage
### Position Type

```{r }
swims.plot.distribution("mainPosition",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups,
                        width_text = 25)
```
\normalsize
`r swims.formulation("mainPosition")`  
Recoded positions into four broad groups: "Researcher aiming for a PhD,", "Postdoctoral researcher", "Other researchers with a PhD", and "Other". "Prefer not to say" responses coded as NA. 
\normalsize

\newpage
### Funding source

```{r }
 swims.plot.distribution("funding",
                         institution_prov = target_institution,
                         font_size = params$font_text,
                         annoFontSize = params$font_anno,
                         cut.small.groups = params$cut_off,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("funding")`  
Original funding categories simplified into three groups: "SNSF", "Non-SNSF funding", and "University/Higher education institute." Ambiguous or undisclosed funding sources coded as missing (NA).
\normalsize

\newpage
### Residence status

```{r }
swims.plot.distribution("residenceStatus",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("residenceStatus")`  
Subsequently used with residence status reduced to two groups: "Swiss citizenship + Permit C", and "Other Permits." Non-disclosed or unclear responses coded as NA.
\normalsize

\newpage
### Care work

```{r}
swims.plot.distribution("Carework",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("careFamily")`  
`r swims.formulation("careKids")`  
Simplified into "care work" (if respondents indicated caring for children/family) or "no care work". Missing or unclear responses were coded as missing.
\normalsize

\newpage
### Other demographic variables
  
These variables will not be used for group comparisons later, thus the name "other".
  
  
#### Employment Status

```{r }
swims.plot.distribution("employmentStatus",
                          institution_prov = target_institution,
                          font_size = params$font_text,
                          annoFontSize = params$font_anno,
                          cut.small.groups = params$cut_off,
                          small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`  
`r swims.formulation("employmentStatus", what = "item")`
\normalsize

\newpage
#### Employment Percentage
  
```{r}
swims.plot.distribution("workloadMainjob",
                          institution_prov = target_institution,
                          font_size = params$font_text,
                          annoFontSize = params$font_anno,
                          cut.small.groups = params$cut_off,
                          small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("employmentStatus", what = "item")`
\normalsize

\newpage
#### Additional Non-Academic Job

```{r}
swims.plot.distribution("nonacademicJob",
                          institution_prov = target_institution,
                          font_size = params$font_text,
                          annoFontSize = params$font_anno,
                          cut.small.groups = params$cut_off,
                          small.group.delete = params$del_small_groups)
```
\normalsize
`r swims.formulation("nonacademicJob", what = "item")`
\normalsize

\newpage
# Mental Health

## General Mental Health

\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.distribution("mentalHealth",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```

\newpage
### General Mental Health by Age
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize
```{r}
swims.plot.distribution("mentalHealth",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### General Mental Health by Gender
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize
```{r}
swims.plot.distribution("mentalHealth",
                         institution_prov = target_institution,
                         divider = "Gender",
                         font_size = params$font_text,
                         annoFontSize = params$font_anno,
                         cut.small.groups = params$cut_off,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
 
\newpage
### General Mental Health by Research Discipline
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize
```{r}
swims.plot.distribution("mentalHealth",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### General Mental Health by Position Type
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize
```{r}
swims.plot.distribution("mentalHealth",
                         institution_prov = target_institution,
                         divider = "Position",
                         font_size = params$font_text,
                         annoFontSize = params$font_anno,
                         cut.small.groups = params$cut_off,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### General Mental Health by Care Work
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize
```{r}
swims.plot.distribution("mentalHealth",
                         institution_prov = target_institution,
                         divider = "Carework",
                         font_size = params$font_text,
                         annoFontSize = params$font_anno,
                         cut.small.groups = params$cut_off,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### General Mental Health by Funding Source
\normalsize
`r swims.formulation("mentalHealth", what = "item")`
\normalsize
```{r}
swims.plot.distribution("mentalHealth",
                         institution_prov = target_institution,
                         divider = "Funding",
                         font_size = params$font_text,
                         annoFontSize = params$font_anno,
                         cut.small.groups = params$cut_off,
                         small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Depression

```{r}
library(psych)

side_obj <- dat %>%
  filter(inst == target_institution) %>%
  select(paste0("depression_", c(1:7)))

del <- which(!complete.cases(side_obj))

side_obj <- side_obj[-del, ]

cronbach <- alpha(side_obj)

```

Sum score of the 7 DASS-21 sub-dimension depression items

For this sample:
  Cronbach's alpha:  `r round(cronbach$total[2],2)`

Removed : `r length(del)` due to at least 1 missing depression item score

Categorization: above score 10 problematic (Nilges \& Essau, 2021)

```{r}
swims.plot.distribution("Depression",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups, 
                        fct_ord = c(0:21))

swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Depression by Age

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Gender

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Research Discipline

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Position Type

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Care Work

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Depression by Funding Source

```{r}
swims.plot.distribution("DepressionCategory",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Burnout
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize
```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Burnout by Age
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize
```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Gender
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize
```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Research Discipline
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize
```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Position Type
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize
```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Care Work
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize
```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Burnout by Funding Source
\normalsize
`r swims.formulation("Burnout", what = "item")`
\normalsize
```{r}
swims.plot.distribution("Burnout",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Awarenes Resources

```{r, out.width = "70%"}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups,
                    alpha_plot = params$alpha_val)
```

\newpage
### Awarenes Resources by Age

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awarenes Resources by Gender

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awarenes Resources by Research Discipline

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awarenes Resources by Position Type

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awarenes Resources by Care Work

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Awarenes Resources by Funding Source

```{r}
swims.plot.multibar("resources",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Job Satisfaction
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize
```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Job Satisfaction by Age
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize
```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Gender
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize
```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Research Discipline
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize
```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Position Type
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize
```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Care Work
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize
```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Job Satisfaction by Funding Source
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize
```{r}
swims.plot.distribution("jobSatisfaction",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Quitting Intentions
\normalsize
`r swims.formulation("jobSatisfaction", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Quitting Intentions by Age
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Gender
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Research Discipline
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Position Type
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Care Work
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Quitting Intentions by Funding Source
\normalsize
`r swims.formulation("quitting", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Stressors
## Stress
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize
```{r}
swims.plot.distribution("stress",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```

\newpage
### Stress by Age
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Gender
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Research Discipline
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Position Type
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Care Work
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Stress by Funding Source
\normalsize
`r swims.formulation("stress", what = "item")`
\normalsize
```{r}
swims.plot.distribution("quitting",
                        institution_prov = target_institution,
                        divider = "Funding",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## System Stressors
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### System Stressors by Age
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Gender
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\newpage
\normalsize
`r imp_mess`
\normalsize
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Research Discipline
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Position Type
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Care Work
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### System Stressors by Funding Source
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("stressFunding", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_system3",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Supervisor Stressors
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Supervisor Stressors by Age
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Gender
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Research Discipline
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Position Type
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Care Work
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor Stressors by Funding Source
\normalsize
`r swims.formulation("stressUnclearExp", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_supervisor",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Colleagues Stressors
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Colleagues Stressors by Age
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Gender
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Research Discipline
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Position Type
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Care Work
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Colleagues Stressors by Funding Source
\normalsize
`r swims.formulation("stressLackSocialIntegr", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_colleagues",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Self-Management Stressors
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Self-Management Stressors by Age
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Gender
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Research Discipline
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Position Type
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Care Work
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Self-Management Stressors by Funding Source
\normalsize
`r swims.formulation("stressLackTrainingSoft", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_selfManagement",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Private Stressors
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Private Stressors by Age
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Gender
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Research Discipline
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Position Type
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Care Work
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Private Stressors by Funding Source
\normalsize
`r swims.formulation("stressPrivate", what = "item")`
\normalsize
```{r}
swims.plot.multibar("stress_private",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Supervisor
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Supervisor by Age
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Gender
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Research Discipline
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Position Type
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Care Work
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Supervisor by Funding Source
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("worklifebalanceSup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("supervisor3",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Institution
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Institution by Age
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Gender
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Research Discipline
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Position Type
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Care Work
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Institution by Funding Source
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize
```{r}
swims.plot.multibar("institution2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)

```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Work-Group
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Work-Group by Age
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Gender
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Research Discipline
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Position Type
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Care Work
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Work-Group by Funding Source
\normalsize
`r swims.formulation("collabWorkinggroup", what = "item")`
\normalsize
```{r}
swims.plot.multibar("workgroup",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
# Discrimination
## Discrimination Experience
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r, out.width = "70%"}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    font_size = (params$font_text + 1),
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```

\newpage
### Discrimination Experience by Age
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Gender
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Research Discipline
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Position Type
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Care Work
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
### Discrimination Experience by Funding Source
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
\normalsize
`r swims.formulation("discriminationWitness", what = "item")`
\normalsize
```{r}
swims.plot.multibar("discrimination2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Sources of Discrimination
\normalsize
`r swims.formulation("discrAge", what = "item")`
\normalsize
```{r}
swims.plot.aggregation("discrimination_type",
                       institution_prov = target_institution,
                       font_size = params$font_text)
```

\newpage
## Amount of Sources of Discrimination
\normalsize
`r swims.formulation("discrAge", what = "item")`
\normalsize
```{r}
swims.plot.aggregation("discrimination_type",
                       institution_prov = target_institution,
                       font_size = (params$font_text + 5),
                       count_votes_at_all = TRUE)
```

\newpage
## Reporting Information
\normalsize
`r swims.formulation("discrAge", what = "item")`
\normalsize
```{r}
swims.plot.distribution("discrReport",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```

\newpage
# Questionable Research Practices
## Performing of QRPs
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Performing of QRPs by Age
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Performing of QRPs by Gender
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Performing of QRPs by Research Discipline
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Performing of QRPs by Position Type
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Performing of QRPs by Care Work
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Performing of QRPs by Funding Source
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp1",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp2",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize
\newpage
\normalsize
`r swims.formulation("qrpFalsdata", what = "item")`
\normalsize
```{r, out.width = "60%"}
swims.plot.multibar("qrp3",
                    institution_prov = target_institution,
                    divider = "Funding",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 2),
                    space4comp = F,
                    legend.nrow = 3,
                    wrap_legend = F,
                    alpha_plot = params$alpha_val,
                    cut.small.groups = params$cut_off,
                    small.group.delete = params$del_small_groups)
```
\normalsize
`r imp_mess`
\normalsize

\newpage
## Source of Pressure
\normalsize
`r swims.formulation("pressureqrpFunder", what = "item")`
\normalsize
```{r}
swims.plot.aggregation("qrp_pressure",
                       institution_prov = target_institution,
                       font_size = params$font_text)
```

\newpage
## Effect on Mental Health
\normalsize
`r swims.formulation("pressureqrpFunder", what = "item")`
\normalsize
```{r}
swims.plot.distribution("pressureqrpMentalhealth",
                        institution_prov = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno,
                        cut.small.groups = params$cut_off,
                        small.group.delete = params$del_small_groups)
```

\newpage
# Appendix

## Codebook

Detailed variable names, item formulations, etc. can be found in the codebook [link]

# References
