---
title: "Institution Report: SWiMS 2024 Data"
author: "actionuni Survey Team"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
bibliography: references.bib 
header-includes:
  - \usepackage{graphicx}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\includegraphics[width=4cm]{actionuni_logo_klein.png}}
  - \fancyhead[C]{}
  - \fancyhead[R]{Institution Report}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(readxl)
```

```{r load-data, include=FALSE}
rm(list = ls())
# Load data
load("../data/SWiMS2024_Data_2025-01-07.RData")
source("99_helpers.R")


# Set target institution index manually
target_index <- 1  # Change this value to select the institution
institution_labels <- strsplit(codebook[codebook$VarName %in% "institution","Labels"],"//")[[1]]
target_institution <- institution_labels[target_index]
remaining_institutions <- setdiff(institution_labels, target_institution)

```

# Introduction

The **SWiMS 2024 Survey** explores the mental health and well-being of mid-level academic staff (e.g., doctoral researchers, scientific associates, postdocs, and other scientific staff) in Switzerland. The goal is to identify problems and areas for improvement in working conditions and research environments. This report focuses on the institution **`r target_institution`**, comparing its responses to those from other institutions.

---
  
  # Sample Description
  
  ## Key Demographics
  
  The table below summarizes the key demographic characteristics of respondents from **`r target_institution`** compared to all other institutions.

```{r sample-description}
# Select demographic variables
demographic_vars <- c("age", "gender", "mainPosition", "researchDiscipline", "phd")

demographics_summary <- dat %>%
  mutate(group = ifelse(institution == target_institution, "Target Institution", "Other Institutions")) %>%
  select(group, all_of(demographic_vars)) %>%
  pivot_longer(cols = all_of(demographic_vars), names_to = "Variable", values_to = "Value") %>%
  group_by(group, Variable, Value) %>%
  summarise(Count = n(), .groups = "drop") %>%
  group_by(group, Variable) %>%
  mutate(Proportion = round(Count / sum(Count),2))

# Create a table
summary_table <- demographics_summary %>%
  pivot_wider(names_from = group, values_from = c(Count, Proportion))

summary_table %>%
  kbl(caption = "Demographic Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

---

# Key Variables

## Job Satisfaction 

Job satisfaction item by @dolbier_reliability_2005. 

```{r job satisfaction}
swims.plot <- function(var, institution = target_institution, category = "distribution", data = dat, codeb = codebook){
  
  if(category == "distribution"){
    # Ensure var exists in the codeb
    if (!var %in% codeb$VarName) {
      stop(paste("Variable", var, "not found in the codeb."))
    }
    
    # Use variable label if available
    x_label <- strsplit(codeb[codeb$VarName %in% var,"Labels"],"//")[[1]]
    
    # Prepare data for plotting
    plot_data <- data %>%
      mutate(group = ifelse(institution == target_institution, paste0(target_institution), "Other Institutions")) %>%
      filter(!is.na(!!sym(var)), !is.na(group)) %>%
      group_by(group, !!sym(var)) %>%
      summarise(count = n(), .groups = "drop") %>%
      group_by(group) %>%
      mutate(proportion = count / sum(count))
    
    # Create plot
    g <- ggplot(plot_data, aes_string(x = var, y = "proportion", fill = "group")) +
      geom_bar(stat = "identity", position = "dodge", width = 0.8) +
      scale_y_continuous(labels = scales::percent, limits = c(0,max(plot_dataa$proportion+.05))) +
      labs(
        x = var,
        y = "Proportion",
        fill = "Institution",
        title = paste("Distribution of", var)
      ) +
      scale_fill_manual(values = c(myblue, myorange)) +
      geom_text(aes(label = count), position = position_dodge(width = 0.8), vjust = -0.5, size = 4) +
      theme_minimal() +
      theme(
        text = element_text(size = 12),
        axis.text.x = element_text(size = 10, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.title = element_text(size = 10),
        plot.title = element_text(size = 14, hjust = 0.5)
      )
  }
  
  
  
  
  plot(g)
}
#swims.plot(var = "jobSatisfaction")

```

## Supervisor
```{r supervisor}

#swims.plot(category = "supervisor")

```

---
  
  # Key Variables
  
  The following plots compare the responses to key survey variables between **`r target_institution`** and all other institutions.

```{r key-variables}
# Select key variables
key_vars <- c("stress", "jobSatisfaction", "burnOut")

# Generate plots
for (var in key_vars) {
  # Use variable label if available
  x_label <- strsplit(codebook[codebook$VarName %in% var,"Labels"],"//")[[1]]
  
  # Prepare data for plotting
  plot_data <- dat %>%
    mutate(group = ifelse(institution == target_institution, paste0(target_institution), "Other Institutions")) %>%
    filter(!is.na(!!sym(var)), !is.na(group)) %>%
    group_by(group, !!sym(var)) %>%
    summarise(count = n(), .groups = "drop") %>%
    group_by(group) %>%
    mutate(proportion = count / sum(count))
  
  # Create plot
  g <- ggplot(plot_data, aes_string(x = var, y = "proportion", fill = "group")) +
    geom_bar(stat = "identity", position = "dodge", width = 0.8) +
    scale_y_continuous(labels = scales::percent, limits = c(0,max(plot_data$proportion+.05))) +
    labs(
      x = var,
      y = "Proportion",
      fill = "Institution",
      title = paste("Distribution of", var)
    ) +
    scale_fill_manual(values = c("#1f77b4", "#ff7f0e")) +
    geom_text(aes(label = count), position = position_dodge(width = 0.8), vjust = -0.5, size = 4) +
    theme_minimal() +
    theme(
      text = element_text(size = 12),
      axis.text.x = element_text(size = 10, angle = 45, hjust = 1),
      axis.text.y = element_text(size = 10),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 10),
      legend.title = element_text(size = 10),
      plot.title = element_text(size = 14, hjust = 0.5)
    )
  
  plot(g)
}
```

---
  
  # Appendix
  
  ## Codebook
  
  The following table provides an overview of the variable names and their corresponding labels.

```{r codebook}
codebook %>%
  kbl(caption = "Codebook") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = TRUE)
