---
title: "Institution Report: SWiMS 2024 Data"
author: "actionuni Survey Team"
date: "`r Sys.Date()`"
params:
  object.inst: 4
  font_text: 16
  font_anno: 6
  fontsize_inplot_text: 8
output:
  pdf_document:
    toc: true
    toc_depth: 3
    keep_tex: true
    fig_caption: false
# bibliography: references.bib 
classoption: landscape
geometry: top=1.5cm, bottom=1.5cm, left=1cm, right=1cm
header-includes:
  - \usepackage{graphicx}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  # - \fancyhead[L]{\includegraphics[width=1.5cm]{actionuni_logo_klein.png}}
  - \fancyhead[C]{}
  - \fancyhead[R]{SWiMS 2024 Institution Report}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = FALSE, message = FALSE,
                      out.width = "75%",
                      fig.width = 16,        
                      fig.height = 14,   
                      fig.align = 'center', 
                      fig.pos = 'H',
                      dpi = 300)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(readxl)
library(dplyr)
```

```{r load-data, include=FALSE}
# Load data
load("../data/SWiMS2024_Data_2025-03-25.RData") # ToDo: wir müssen unbedingt drauf achten dass alles nutzbar ist für beide ich kann data cleaningn icht nutzen weil mir ien objekt fehlt
source("99_helpers.R")


# Set target institution index manually
target_index <- params$object.inst  # Change this value to select the institution
institution_labels <- strsplit(codebook[codebook$VarName %in% "institution","Labels"],"//")[[1]]
target_institution <- institution_labels[target_index]
remaining_institutions <- setdiff(institution_labels, target_institution)

```

# Introduction

The **SWiMS 2024 Survey** explores the mental health and well-being of mid-level academic staff (e.g., doctoral researchers, scientific associates, postdocs, and other scientific staff) in Switzerland. The goal is to identify problems and areas for improvement in working conditions and research environments. This report focuses on the institution **`r target_institution`**, comparing its responses to those from other institutions.

---
  
# Sample Description

## Response Rate

```{r}

institution_counts <- dat %>%
  group_by(inst) %>%
  summarise(count = n()) %>%
  filter(count > 10)

institution_counts <- institution_counts %>%
  left_join(dat.meta %>% select(Name, Members), by = c("inst" = "Name")) # add member numbers
institution_counts$response_rate <- institution_counts$count/institution_counts$Members



```

`r institution_counts[institution_counts$inst %in% target_institution,"count"]` responses were collected from `r target_institution` with a total number of members estimated at `r institution_counts[institution_counts$inst %in% target_institution,"Members"]` (taken from the actionuni reports on memberships), corresponding to a participation rate of `r round(institution_counts[institution_counts$inst %in% target_institution,"response_rate"]*100,1)`%.


## Demographics

The figures below summarize the key demographic characteristics of all parttaking institutions.

### Age

```{r age}
swims.plot.distribution("age",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### Gender

```{r gender}
swims.plot.distribution("Gender",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### Research Discipline

```{r }
swims.plot.distribution("Discipline",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)

```

### Position Type

```{r }
swims.plot.distribution("mainPosition",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### Funding source

```{r }
swims.plot.distribution("funding",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```


### Residence status

```{r }
swims.plot.distribution("residenceStatus",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### Care work

```{r}
swims.plot.distribution("Carework",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### Other demographic variables

These variables will not be used for group comparisons later, thus the name "other".

<!-- \newpage -->
#### Employment Status

```{r }
swims.plot.distribution("employmentStatus",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

<!-- \newpage -->
#### Employment Percentage

```{r}
swims.plot.distribution("workloadMainjob",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

\newpage
#### Additional Non-Academic Job

```{r}
swims.plot.distribution("nonacademicJob",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)

```

\newpage
# Mental Health

## General Mental Health

Overall Distribution
```{r}
swims.plot.distribution("mentalHealth",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```



### General Mental Health by Age

```{r}
swims.plot.distribution("mentalHealth",
                        institution = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### General Mental Health by Gender

```{r}
swims.plot.distribution("mentalHealth",
                        institution = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### General Mental Health by Research Discipline

```{r}
swims.plot.distribution("mentalHealth",
                        institution = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### General Mental Health by Position Type

```{r}
swims.plot.distribution("mentalHealth",
                        institution = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```


### General Mental Health by Care Work

```{r}
swims.plot.distribution("mentalHealth",
                        institution = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

## Depression

Overall Distribution
```{r}
swims.plot.distribution("Depression",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)

swims.plot.multibar("depression",
                    institution = target_institution,
                    font_size = params$font_text,
                    fontsize_inplot = params$fontsize_inplot_text,
                    legend.nrow = 2)

```



### Depression by Age

```{r}
swims.plot.distribution("Depression",
                        institution = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)

swims.plot.multibar("depression",
                    institution = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 3),
                    space4comp = T,
                    legend.nrow = 4,
                    wrap_legend = T)
```

### Depression by Gender

```{r}
swims.plot.distribution("Depression",
                        institution = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)

swims.plot.multibar("depression",
                    institution = target_institution,
                    divider = "Gender",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 3),
                    space4comp = T,
                    legend.nrow = 4,
                    wrap_legend = T)
```

### Depression by Research Discipline

```{r}
swims.plot.distribution("Depression",
                        institution = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)

swims.plot.multibar("depression",
                    institution = target_institution,
                    divider = "Discipline",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 3),
                    space4comp = T,
                    legend.nrow = 4,
                    wrap_legend = T)
```

### Depression by Position Type

```{r}
swims.plot.distribution("Depression",
                        institution = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)

swims.plot.multibar("depression",
                    institution = target_institution,
                    divider = "Position",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 3),
                    space4comp = T,
                    legend.nrow = 4,
                    wrap_legend = T)
```


### Depression by Care Work

```{r}
swims.plot.distribution("Depression",
                        institution = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)

swims.plot.multibar("depression",
                    institution = target_institution,
                    divider = "Carework",
                    font_size = params$font_text,
                    fontsize_inplot = (params$fontsize_inplot_text - 3),
                    space4comp = F,
                    legend.nrow = 4,
                    wrap_legend = T)
```

## Burnout

Overall Distribution
```{r}
swims.plot.distribution("Burnout",
                        institution = target_institution,
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```



### Burnout by Age

```{r}
swims.plot.distribution("Burnout",
                        institution = target_institution,
                        divider = "Age",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### Burnout by Gender

```{r}
swims.plot.distribution("Burnout",
                        institution = target_institution,
                        divider = "Gender",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### Burnout by Research Discipline

```{r}
swims.plot.distribution("Burnout",
                        institution = target_institution,
                        divider = "Discipline",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

### Burnout by Position Type

```{r}
swims.plot.distribution("Burnout",
                        institution = target_institution,
                        divider = "Position",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```


### Burnout by Care Work

```{r}
swims.plot.distribution("Burnout",
                        institution = target_institution,
                        divider = "Carework",
                        font_size = params$font_text,
                        annoFontSize = params$font_anno)
```

## Awarenes Resources

Overall Distribution
```{r}
swims.plot.multibar("resources",
                    institution = target_institution,
                    font_size = params$font_text,
                    fontsize_inplot = params$fontsize_inplot_text)
```


### Awarenes Resources by Age

```{r}
swims.plot.multibar("resources",
                    institution = target_institution,
                    divider = "Age",
                    font_size = params$font_text,
                    fontsize_inplot = params$fontsize_inplot_text)
```

<!-- ### Awarenes Resources by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("resources", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Awarenes Resources by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("resources", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Awarenes Resources by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("resources", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Awarenes Resources by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("resources", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ## Job Satisfaction -->

<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.distribution("jobSatisfaction", -->
<!--                         institution = target_institution, -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->



<!-- ### Job Satisfaction by Age -->

<!-- ```{r} -->
<!-- swims.plot.distribution("jobSatisfaction", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Age", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ### Job Satisfaction by Gender -->

<!-- ```{r} -->
<!-- swims.plot.distribution("jobSatisfaction", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Gender", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ### Job Satisfaction by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.distribution("jobSatisfaction", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Discipline", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ### Job Satisfaction by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.distribution("jobSatisfaction", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Position", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->


<!-- ### Job Satisfaction by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.distribution("jobSatisfaction", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Carework", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ## Quitting Intentions -->

<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.distribution("quitting", -->
<!--                         institution = target_institution, -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->



<!-- ### Quitting Intentions by Age -->

<!-- ```{r} -->
<!-- swims.plot.distribution("quitting", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Age", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ### Quitting Intentions by Gender -->

<!-- ```{r} -->
<!-- swims.plot.distribution("quitting", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Gender", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ### Quitting Intentions by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.distribution("quitting", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Discipline", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ### Quitting Intentions by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.distribution("quitting", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Position", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->


<!-- ### Quitting Intentions by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.distribution("quitting", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Carework", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- # Stressors -->

<!-- ## Stress -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.distribution("stress", -->
<!--                         institution = target_institution, -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->



<!-- ### Stress by Age -->

<!-- ```{r} -->
<!-- swims.plot.distribution("stress", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Age", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ### Stress by Gender -->

<!-- ```{r} -->
<!-- swims.plot.distribution("stress", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Gender", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ### Stress by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.distribution("stress", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Discipline", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ### Stress by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.distribution("stress", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Position", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->


<!-- ### Stress by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.distribution("stress", -->
<!--                         institution = target_institution, -->
<!--                         divider = "Carework", -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ## System Stressors -->

<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("stress_system", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### System Stressors by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_system", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### System Stressors by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_system", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### System Stressors by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_system", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### System Stressors by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_system", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### System Stressors by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_system", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ## Supervisor Stressors -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("stress_supervisor", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Supervisor Stressors by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Supervisor Stressors by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Supervisor Stressors by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Supervisor Stressors by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Supervisor Stressors by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ## Colleagues -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("stress_colleagues", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Colleagues Stressors by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_colleagues", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Colleagues Stressors by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_colleagues", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Colleagues Stressors by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_colleagues", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Colleagues Stressors by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_colleagues", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Colleagues Stressors by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_colleagues", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ## Self-Management Stressors -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("stress_selfManagement", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Self-Management Stressors by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_selfManagement", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Self-Management Stressors by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_selfManagement", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Self-Management Stressors by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_selfManagement", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Self-Management Stressors by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_selfManagement", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Self-Management Stressors by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_selfManagement", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->



<!-- ## Private Stressors -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("stress_private", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Private Stressors by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_private", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Private Stressors by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_private", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Private Stressors by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_private", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Private Stressors by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_private", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Private Stressors by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("stress_private", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->



<!-- # Supervisor -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("supervisor", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Supervisor by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Supervisor by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Supervisor by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Supervisor by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Supervisor by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("supervisor", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- # Institution -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("institution", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Institution by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("institution", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Institution by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("institution", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Institution by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("institution", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Institution by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("institution", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Institution by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("institution", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- # Work-Group -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("workgroup", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Work-Group by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("workgroup", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Work-Group by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("workgroup", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Work-Group by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("workgroup", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Work-Group by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("workgroup", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Work-Group by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("workgroup", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- # Discrimination -->

<!-- ## Discrimination Experience -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("discrimination", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Discrimination Experience by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("discrimination", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Discrimination Experience by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("discrimination", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Discrimination Experience by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("discrimination", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Discrimination Experience by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("discrimination", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Discrimination Experience by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("discrimination", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ## Discrimination Dimensions -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.aggregation("discrimination_type", -->
<!--                        institution = target_institution, -->
<!--                        font_size = params$font_text, -->
<!--                        annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ## Reporting Information -->

<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.distribution("discrReport", -->
<!--                         institution = target_institution, -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- # Questionable Research Practices -->
<!-- ## Performing of QRPs -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.multibar("qrp", -->
<!--                     institution = target_institution, -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Performing of QRPs by Age -->

<!-- ```{r} -->
<!-- swims.plot.multibar("qrp", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Age", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Performing of QRPs by Gender -->

<!-- ```{r} -->
<!-- swims.plot.multibar("qrp", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Gender", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Performing of QRPs by Research Discipline -->

<!-- ```{r} -->
<!-- swims.plot.multibar("qrp", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Discipline", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->

<!-- ### Performing of QRPs by Position Type -->

<!-- ```{r} -->
<!-- swims.plot.multibar("qrp", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Position", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->


<!-- ### Performing of QRPs by Care Work -->

<!-- ```{r} -->
<!-- swims.plot.multibar("qrp", -->
<!--                     institution = target_institution, -->
<!--                     divider = "Carework", -->
<!--                     font_size = params$font_text, -->
<!--                     fontsize_inplot = params$fontsize_inplot_text) -->
<!-- ``` -->



<!-- ## Source of Pressure -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.aggregation("qrp_pressure", -->
<!--                        institution = target_institution, -->
<!--                        font_size = params$font_text, -->
<!--                        annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- ## Effect on Mental Health -->
<!-- Overall Distribution -->
<!-- ```{r} -->
<!-- swims.plot.distribution("pressureqrpMentalhealth", -->
<!--                         institution = target_institution, -->
<!--                         font_size = params$font_text, -->
<!--                         annoFontSize = params$font_anno) -->
<!-- ``` -->

<!-- # Appendix -->

<!-- ## Codebook -->

<!-- Detailed variable names, item formulations, etc. can be found in the codebook [link] -->

<!-- # References -->
