---
title: "National Report: SWiMS 2024 Data"
author: "actionuni Survey Team"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
header-includes:
  - \usepackage{graphicx}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\includegraphics[width=1.5cm]{actionuni_logo_klein.png}}
  - \fancyhead[C]{}
  - \fancyhead[R]{SWiMS 2024 National Report}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(readxl)
```

```{r load-data, include=FALSE}
rm(list = ls())
# Load data
load("../data/SWiMS2024_Data_2025-03-18.RData")
source("99_helpers.R")


institution_labels <- strsplit(codebook[codebook$VarName %in% "institution","Labels"],"//")[[1]]

```

# Introduction


The SWiMS 2024 Survey examines the mental health and well-being of mid-level academic staff across Switzerland, including doctoral researchers, scientific associates, and postdocs. The survey aims to identify key challenges in working conditions and research environments, providing a data-driven foundation for improving policies and support systems at Swiss higher education institutions (HEIs).

This report presents the national-level findings, offering insights into stressors, mental health outcomes, and available resources. By highlighting systemic issues and institutional differences, the data provide a basis for further discussions on how to improve well-being in academia.

## Background and Motivation
Mid-level academic staff are essential to research, teaching, and student supervision, making up approximately 48% of the academic workforce in Switzerland (Federal Statistical Office, 2024). Despite their crucial role, many experience high levels of stress and job insecurity, which can negatively impact both their mental health and the quality of academic work.

Several factors contribute to these challenges, including intense workload, administrative responsibilities, publication pressure, and uncertain career prospects due to the prevalence of temporary contracts. These stressors are well-documented in international research, with studies indicating that 30-40% of early career researchers report mental health issues (Divaris et al., 2012; Gloria & Steinhardt, 2016; Levecque et al., 2017; Evans et al., 2018). Burnout, depression, and anxiety are particularly prevalent, threatening both individual well-being and the sustainability of academic careers (Bolotnyy et al., 2022; Boone et al., 2022; Satinsky et al., 2021).

Despite growing awareness of these issues, Switzerland lacks comprehensive national data on the mental health of mid-level academic staff. While some institutions have conducted internal surveys (e.g., ETH Zurich’s employee survey), a coordinated, nationwide effort has been missing. The reluctance of universities to engage in comparisons—possibly due to reputational concerns—may contribute to this gap. Yet, without broad-based data, it is difficult to develop effective interventions or institution-wide improvements.

## The Swiss-Wide Mental Health Survey (SWiMS)

To address this gap, actionuni, in collaboration with 12 mid-level academic staff associations, launched SWiMS 2024 as a bottom-up initiative. The survey provides the first nationwide assessment of mental health among early career researchers in Switzerland, highlighting both stressors and protective factors.

By systematically analyzing the collected data, the project aims to:

- Expand the knowledge base on mental health in academia.
- Identify key stress factors affecting mid-level academic staff.
- Enable institutions to learn from best practices, improving support systems.
- Provide an evidence-based foundation for discussions on mental health policies.

Ultimately, fostering a healthier academic work environment benefits not only early career researchers but also research quality, institutional innovation, and the broader university system. Ensuring well-being at all career stages is essential for maintaining the long-term excellence and sustainability of Swiss academia.


---
  
# Sample Description

## Data cleaning 
Only institutions with more than 10 responses were considered in this report. 43 participants of 16 institution with a mean of 2.7 (SD = 1.81) participants were removed from the dataset. 62 additional responses were removed because institution "Other" (n = 44), "Prefer not to say" (n = 15), or were missing (n = 3) were indicated. We also exculded participants that took shorter than 4 minutes to respond (n = 4). In total, `r nrow(dat)` responses were part of this report.  


## Parttaking institutions and response

```{r, echo = F}

# Calculate the number of participants for each institution
institution_counts <- dat %>%
  group_by(inst) %>%
  summarise(count = n()) %>%
  filter(count > 10)

# Filter the data to include only institutions with more than 20 participants
filtered_dat <- dat %>%
  filter(inst %in% institution_counts$inst)

# Get the maximum count to set y-axis limit
max_count <- max(institution_counts$count)
sum_count <- sum(institution_counts$count)

# Create the plot
ggplot(filtered_dat, aes(x = reorder(factor(inst), table(inst)[factor(inst)]), y = ..count..)) +  
  geom_bar(fill = "steelblue", alpha = 0.7) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.title.y = element_text(size = 12, face = "bold"),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.caption = element_text(size = 8, hjust = 0.5, face = "italic")
  ) +
  labs(
   # title = "Number of Responses by Institution",
    x = "Institution Name",
    y = "Number of Responses",
    caption = paste("Total count: ",sum_count ,"\n",
                    "Only institutions with more than 10 participants are displayed.")
  ) +
  geom_text(stat = 'count', aes(label = ..count..), hjust = -0.1, size = 3.5) +
  ylim(c(0, max_count + 30)) +
  coord_flip()

#ggsave(paste0("../plots/SWiMS_responses_",date ,".pdf"), height = 7, width = 8)
```

The average duration of responding to the survey was `r round(mean(dat[dat$duration < 2*3600,"duration"]/60, na.rm =T),2)` minutes (SD = `r round(sd(dat[dat$duration < 2*3600,"duration"]/60, na.rm =T),2)`).

### Response Rate

TODO: do we want to do this? it will just look bad!

```{r}

institution_counts <- institution_counts %>%
  left_join(dat.meta %>% select(Name, Members), by = c("inst" = "Name")) # add member numbers
institution_counts$response_rate <- institution_counts$count/institution_counts$Members

# Create the bar chart
ggplot(institution_counts, aes(x = reorder(inst, count))) + 
  geom_bar(aes(y = Members), stat = "identity", fill = "lightgray", alpha = 0.7) + 
  geom_bar(aes(y = count), stat = "identity", fill = "steelblue", alpha = 0.7) + 
  geom_text(aes(y = count, label = sprintf("%.1f%%", response_rate * 100)), 
            hjust = -0.1, size = 3.5) +
  labs(x = "Institution Name", 
       y = "Number of estimated Members (in gray)\n and Responses (in blue)") + 
  theme_minimal(base_size = 12) + 
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 12, face = "bold"),
    axis.title.y = element_text(size = 12, face = "bold"),
    plot.caption = element_text(size = 8, hjust = 0.5, face = "italic")
  ) +
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)))

#ggsave(paste0("../plots/SWiMS_response_rate_",Sys.Date(),".pdf"), height = 7, width = 8)

```


## Sample description 
  
The figures below summarize the key demographic characteristics of all parttaking institutions.

### Age

```{r age}
swims.plot.distribution("age")
```
### Gender

```{r gender}
swims.plot.distribution("gender")
```

### Research Discipline

```{r }
swims.plot.distribution("researchDiscipline") 

```

### Position Type

```{r }
swims.plot.distribution("mainPosition")  + 
    scale_x_discrete(labels = function(x) str_wrap(x, width = 23))   # Apply text wrapping

```

### Funding soruce

```{r }
swims.plot.distribution("funding")
```


### Residence status

```{r }
swims.plot.distribution("residenceStatus")
```

### Care work

```{r }
swims.plot.distribution("carework")
```

### Other demographic variables

These variables will not be used for group comparisons later, thus the name "other".

#### Employment Status

```{r }
swims.plot.distribution("employmentStatus")
```
@ Zoran: Do you think we should fix the y-axis to 0% to 100% percent? I think it is fine like this. But it is not so "neutral" then.

#### Employment Percentage

```{r }
swims.plot.distribution("workloadMainjob")
```


#### Additional Non-Academic Job  

```{r }
swims.plot.distribution("nonacademicJob")
```

---
  
# Key Variables

## Job Satistfaction

```{r Job Satistfaction}

swims.plot.distribution("jobSatisfaction")

```
Item formulation: 

*Taking everything into consideration, how satisfied do you feel about your job as a whole?*

item by Dolbier et al., 2005 (REF)

## Institution

```{r Institution}
swims.plot.multibar(var = "institution", colors_set = "RdYlGn")
```

## Workgroup

These workgroup-related were answered if they indicated to be in a working group `r round(100*table(dat$workingGroup)/sum(table(dat$workingGroup)),2)[1]`% (n = `r table(dat$workingGroup)[1]`) of the respondents.

```{r Workgroup}

swims.plot.multibar(var = "workgroup", colors_set = "RdYlGn")
```

## Supervisor

```{r Supervisor}

swims.plot.multibar(var = "supervisor", colors_set = "RdYlGn")
```


## Discrimination

```{r Discrimination}

#swims.plot.multibar(var = "discrmination", colors_set = "RdYlGn")
```


  
# Appendix
  
## Codebook
  
Detailed variable names, item formulations, etc. can be found in the codebook [link]

