---
title: "National Report: SWiMS 2024 Data"
author: "actionuni Survey Team"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
classoption: landscape
header-includes:
  - \usepackage{graphicx}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\includegraphics[width=1.5cm]{actionuni_logo_klein.png}}
  - \fancyhead[C]{}
  - \fancyhead[R]{SWiMS 2024 National Report}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = FALSE, message = FALSE,
                      fig.width = 9, 
                      fig.height = 5, 
                      out.width = "100%", 
                      dpi = 300)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(readxl)
```

```{r load-data, include=FALSE}
rm(list = ls())
# Load data
load("../data/SWiMS2024_Data_2025-03-25.RData")
source("99_helpers.R")


institution_labels <- strsplit(codebook[codebook$VarName %in% "institution","Labels"],"//")[[1]]

```

# Executive Summary

# Introduction


The SWiMS 2024 Survey examines the mental health and well-being of mid-level academic staff across Switzerland, including doctoral researchers, scientific associates, and postdocs. The survey aims to identify key challenges in working conditions and research environments, providing a data-driven foundation for improving policies and support systems at Swiss higher education institutions (HEIs).

This report presents the national-level findings, offering insights into stressors, mental health outcomes, and available resources. By highlighting systemic issues and institutional differences, the data provide a basis for further discussions on how to improve well-being in academia.

## Background and Motivation
Mid-level academic staff are essential to research, teaching, and student supervision, making up approximately 48% of the academic workforce in Switzerland (Federal Statistical Office, 2024). Despite their crucial role, many experience high levels of stress and job insecurity, which can negatively impact both their mental health and the quality of academic work.

Several factors contribute to these challenges, including intense workload, administrative responsibilities, publication pressure, and uncertain career prospects due to the prevalence of temporary contracts. These stressors are well-documented in international research, with studies indicating that 30-40% of early career researchers report mental health issues (Divaris et al., 2012; Gloria & Steinhardt, 2016; Levecque et al., 2017; Evans et al., 2018). Burnout, depression, and anxiety are particularly prevalent, threatening both individual well-being and the sustainability of academic careers (Bolotnyy et al., 2022; Boone et al., 2022; Satinsky et al., 2021).

Despite growing awareness of these issues, Switzerland lacks comprehensive national data on the mental health of mid-level academic staff. While some institutions have conducted internal surveys (e.g., ETH Zurich’s employee survey), a coordinated, nationwide effort has been missing. The reluctance of universities to engage in comparisons—possibly due to reputational concerns—may contribute to this gap. Yet, without broad-based data, it is difficult to develop effective interventions or institution-wide improvements.

## The Swiss-Wide Mental Health Survey (SWiMS)

To address this gap, actionuni, in collaboration with 12 mid-level academic staff associations, launched SWiMS 2024 as a bottom-up initiative. The survey provides the first nationwide assessment of mental health among early career researchers in Switzerland, highlighting both stressors and protective factors.

By systematically analyzing the collected data, the project aims to:

- Expand the knowledge base on mental health in academia.
- Identify key stress factors affecting mid-level academic staff.
- Enable institutions to learn from best practices, improving support systems.
- Provide an evidence-based foundation for discussions on mental health policies.

Ultimately, fostering a healthier academic work environment benefits not only early career researchers but also research quality, institutional innovation, and the broader university system. Ensuring well-being at all career stages is essential for maintaining the long-term excellence and sustainability of Swiss academia.


---
  
# Sample Description

## Data cleaning 
Only institutions with more than 10 responses were considered in this report. 43 participants of 16 institution with a mean of 2.7 (SD = 1.81) participants were removed from the dataset. 62 additional responses were removed because institution "Other" (n = 44), "Prefer not to say" (n = 15), or were missing (n = 3) were indicated. We also exculded participants that took shorter than 4 minutes to respond (n = 4). In total, `r nrow(dat)` responses were part of this report.  


## Parttaking institutions and response

```{r, echo = F}

# Calculate the number of participants for each institution
institution_counts <- dat %>%
  group_by(inst) %>%
  summarise(count = n()) %>%
  filter(count > 10)

# Filter the data to include only institutions with more than 20 participants
filtered_dat <- dat %>%
  filter(inst %in% institution_counts$inst)

# Get the maximum count to set y-axis limit
max_count <- max(institution_counts$count)
sum_count <- sum(institution_counts$count)

# Create the plot
ggplot(filtered_dat, aes(x = reorder(factor(inst), table(inst)[factor(inst)]), y = ..count..)) +  
  geom_bar(fill = "steelblue", alpha = 0.7) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.caption = element_text(size = 8, hjust = 0.5, face = "italic")
  ) +
  labs(
   # title = "Number of Responses by Institution",
    x = "Institution Name",
    y = "Number of Responses",
    caption = paste("Total count: ",sum_count ,"\n",
                    "Only institutions with more than 10 participants are displayed.")
  ) +
  geom_text(stat = 'count', aes(label = ..count..), hjust = -0.1, size = 3.5) +
  ylim(c(0, max_count + 30)) +
  coord_flip()

#ggsave(paste0("../plots/SWiMS_responses_",date ,".pdf"), height = 7, width = 8)
```

The average duration of responding to the survey was `r round(mean(dat[dat$duration < 2*3600,"duration"]/60, na.rm =T),2)` minutes (SD = `r round(sd(dat[dat$duration < 2*3600,"duration"]/60, na.rm =T),2)`).

### Response Rate

```{r}

institution_counts <- institution_counts %>%
  left_join(dat.meta %>% select(Name, Members), by = c("inst" = "Name")) # add member numbers
institution_counts$response_rate <- institution_counts$count/institution_counts$Members

# Create the bar chart
ggplot(institution_counts, aes(x = reorder(inst, count))) + 
  geom_bar(aes(y = Members), stat = "identity", fill = "lightgray", alpha = 0.7) + 
  geom_bar(aes(y = count), stat = "identity", fill = "steelblue", alpha = 0.7) + 
  geom_text(aes(y = count, label = sprintf("%.1f%%", response_rate * 100)), 
            hjust = -0.1, size = 3.5) +
  labs(x = "Institution Name", 
       y = "Number of estimated Members (in gray)\n and Responses (in blue)") + 
  theme_minimal(base_size = 12) + 
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    plot.caption = element_text(size = 8, hjust = 0.5, face = "italic")
  ) +
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)))

#ggsave(paste0("../plots/SWiMS_response_rate_",Sys.Date(),".pdf"), height = 7, width = 8)

```

\newpage

## Demographics 
  
The figures below summarize the key demographic characteristics of all parttaking institutions.

### Age

```{r age, fig.height = 4, fig.width=3}
swims.plot.distribution("age")
```


Grouped original age brackets into three categories: "18-30," "31-40," and ">41." Respondents unwilling to disclose their age were coded as missing.






### Gender

```{r gender, fig.height = 4, fig.width=3}
swims.plot.distribution("Gender")
```



Recoded from multiple binary selections into categories: "male," "female," or "other" (including nonbinary or multiple selections). Ambiguous responses were coded as missing (NA).

### Research Discipline

```{r , fig.height = 5, fig.width=7}
swims.plot.distribution("researchDiscipline") 

```

Subsequently referred to as "Natural Sciences and Engineering", "Medicine", "Social Sciences", and "Humanities". "Prefer not to say" responses coded as NA.

### Position Type

```{r , fig.height = 4, fig.width=8.5}
swims.plot.distribution("mainPosition") # + 
    #scale_x_discrete(labels = function(x) str_wrap(x, width = 23))   # Apply text wrapping

```

Recoded positions into three broad groups: "Researcher aiming for a PhD,", "Researcher with a PhD", and "Other". "Prefer not to say" responses coded as NA.

### Funding Soruce

```{r , fig.height = 4, fig.width=7}
swims.plot.distribution("funding")
```


Original funding categories simplified into three groups: "SNSF", "Non-SNSF funding", and "University/Higher education institute." Ambiguous or undisclosed funding sources coded as missing (NA).

### Residence Status

```{r , fig.height = 4, fig.width=7}
swims.plot.distribution("residenceStatus")
```

Subsequently used with residence status reduced to two groups: "Swiss citizenship + Permit C", and "Other Permits." Non-disclosed or unclear responses coded as NA.


### Care work

```{r , fig.height = 4, fig.width=3}
swims.plot.distribution("Carework")
```

Simplified into "care work" (if respondents indicated caring for children/family) or "no care work". Missing or unclear responses were coded as missing.
\newpage
### Other Demographic Variables

These variables will not be used for group comparisons later, thus the name "other".

#### Employment Status
\

```{r , fig.height =3, fig.width=3}

swims.plot.distribution("employmentStatus")

```


#### Employment Percentage
\

```{r,  fig.height = 3, fig.width=8.5}

swims.plot.distribution("workloadMainjob")

```


#### Additional Non-Academic Job  
\

```{r, fig.height= 3 , fig.width= 4}

swims.plot.distribution("nonacademicJob")

```

# Mental Health

## General Mental Health


```{r mental health, fig.height= 4 , fig.width= 5}
swims.plot.distribution("mentalHealth")
```


### General Mental Health by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "mentalHealth", divider = "Age", annoFontSize = 3)
```

### General Mental Health by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "mentalHealth", divider = "Gender", annoFontSize = 3)
```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### General Mental Health by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "mentalHealth", divider = "Discipline", annoFontSize = 2)
```

### General Mental Health by Funding Source (national only)

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "mentalHealth", divider = "Funding", annoFontSize = 2)
```

### General Mental Health by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "mentalHealth", divider = "Position", annoFontSize = 2)
```


### General Mental Health by Care Work

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "mentalHealth", divider = "Carework", annoFontSize = 3)

```


### General Mental Health by Residence (national only)

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "mentalHealth", divider = "Residence", annoFontSize = 3)

```

## Depression

sum score of the 7 DASS-21 items
with chronbach's alpha of .91 in this sample

62 observations removed due to at least 1 missing depression item score

above score 10 problematic (Nilges, P. \& Essau, C. (2021))

```{r depression, fig.height= 4 , fig.width= 5}
swims.plot.distribution("Depression")

swims.plot.distribution("DepressionCategory")
```

### Depression by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "DepressionCategory", divider = "Age", annoFontSize = 3)
```

### Depression by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "DepressionCategory", divider = "Gender", annoFontSize = 3)
```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Depression by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "DepressionCategory", divider = "Discipline", annoFontSize = 2)
```

### Depression by Funding Source (national only)

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "DepressionCategory", divider = "Funding", annoFontSize = 2)
```

### Depression by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "DepressionCategory", divider = "Position", annoFontSize = 2)
```


### Depression by Care Work

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "DepressionCategory", divider = "Carework", annoFontSize = 3)

```


### Depression by Residence (national only)

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "DepressionCategory", divider = "Residence", annoFontSize = 3)

```

## Burnout

item from REF

```{r burnout, fig.height= 5 , fig.width= 6}
swims.plot.distribution("Burnout")

```


### Burnout by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "Burnout", divider = "Age", annoFontSize = 3)
```

### Burnout by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "Burnout", divider = "Gender", annoFontSize = 3)
```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Burnout by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "Burnout", divider = "Discipline", annoFontSize = 2)
```

### Burnout by Funding Source (national only)

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "Burnout", divider = "Funding", annoFontSize = 2)
```

### Burnout by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "Burnout", divider = "Position", annoFontSize = 2)
```


### Burnout by Care Work

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "Burnout", divider = "Carework", annoFontSize = 3)

```


### Burnout by Residence (national only)

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "Burnout", divider = "Residence", annoFontSize = 3)

```

## Awarenes Resources 

```{r awareness resources, fig.height= 5 , fig.width= 6}
swims.plot.multibar("resources")

```

### Awarenes Resources by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.multibar(var = "resources", divider = "Age")
```

### Awarenes Resources by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.multibar(var = "resources", divider = "Gender")
```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Awarenes Resources by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.multibar(var = "resources", divider = "Discipline")
```

### Awarenes Resources by Funding Source (national only)

```{r, fig.height= 5, fig.width= 8}
swims.plot.multibar(var = "resources", divider = "Funding")
```

### Awarenes Resources by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.multibar(var = "resources", divider = "Position")
```


### Awarenes Resources by Care Work

```{r, fig.height= 5, fig.width= 8}
swims.plot.multibar(var = "resources", divider = "Carework")

```


### Awarenes Resources by Residence (national only)

```{r, fig.height= 5, fig.width= 7}
swims.plot.multibar(var = "resources", divider = "Residence")

```


# Job Satisfaction 

Item formulation: 

*Taking everything into consideration, how satisfied do you feel about your job as a whole?*

item by @dolbier_reliability_2005. 


```{r job satisfaction, fig.height= 5 , fig.width= 6}
swims.plot.distribution("jobSatisfaction")

```


### Job Satisfaction  by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "jobSatisfaction", divider = "Age", annoFontSize = 3)
```

### Job Satisfaction  by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "jobSatisfaction", divider = "Gender", annoFontSize = 3)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Job Satisfaction  by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "jobSatisfaction", divider = "Discipline", annoFontSize = 2)
```

### Job Satisfaction  by Funding Source (national only)

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "jobSatisfaction", divider = "Funding", annoFontSize = 2)
```

### Job Satisfaction  by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "jobSatisfaction", divider = "Position", annoFontSize = 2)
```


### Job Satisfaction  by Care Work

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "jobSatisfaction", divider = "Carework", annoFontSize = 3)

```


### Job Satisfaction  by Residence (national only)

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "jobSatisfaction", divider = "Residence", annoFontSize = 3)

```


## Quitting Intentions


```{r quitting intentions, fig.height= 5 , fig.width= 6}
swims.plot.distribution("quitting")

```


### Quitting Intentions by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "quitting", divider = "Age", annoFontSize = 3)
```

### Quitting Intentions by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "quitting", divider = "Gender", annoFontSize = 3)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Quitting Intentions by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "quitting", divider = "Discipline", annoFontSize = 2)
```

### Quitting Intentions by Funding Source (national only)

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "quitting", divider = "Funding", annoFontSize = 2)
```

### Quitting Intentions by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "quitting", divider = "Position", annoFontSize = 2)
```


### Quitting Intentions by Care Work

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "quitting", divider = "Carework", annoFontSize = 3)

```


### Quitting Intentions by Residence (national only)

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "quitting", divider = "Residence", annoFontSize = 3)

```

# Stressors

## System


To what degree is the following causing you stress currently?

```{r stress system, fig.height= 6 , fig.width= 8}

multibar.fontSize = 8
multibar.fontSizeInplot = 2.5

swims.plot.multibar("stress_system",font_size = multibar.fontSize)

```


### Stressor System by Age


```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_system", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor System by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_system", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor System by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_system", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor System by Funding Source (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_system", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor System by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_system", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


### Stressor System by Care Work

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_system", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


### Stressor System by Residence (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_system", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

## Supervisor

To what degree is the following causing you stress currently?

```{r stress supervisor, fig.height= 6 , fig.width= 8}

swims.plot.multibar("stress_supervisor",font_size = multibar.fontSize)

```


### Stressor Supervisor by Age

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Supervisor by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor Supervisor by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Supervisor by Funding Source (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Supervisor by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


### Stressor Supervisor by Care Work

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


### Stressor Supervisor by Residence (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

## Colleagues


To what degree is the following causing you stress currently?


```{r stress colleagues, fig.height= 6 , fig.width= 8}

swims.plot.multibar("stress_colleagues",font_size = multibar.fontSize)

```


### Stressor Colleagues by Age

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Colleagues by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor Colleagues by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Colleagues by Funding Source (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Colleagues by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


### Stressor Colleagues by Care Work

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


### Stressor Colleagues by Residence (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Self-Management

To what degree is the following causing you stress currently?



```{r stress selfManagement, fig.height= 6 , fig.width= 8}

swims.plot.multibar("stress_selfManagement",font_size = multibar.fontSize)

```


### Stressor Self-Management by Age

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Self-Management by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor Self-Management by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Self-Management by Funding Source (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Self-Management by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


### Stressor Self-Management by Care Work

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


### Stressor Self-Management by Residence (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Private

To what degree is the following causing you stress currently?


```{r stress private, fig.height= 6 , fig.width= 8}

swims.plot.multibar("stress_private",font_size = multibar.fontSize)

```


### Stressor Private by Age

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Private by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor Private by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Private by Funding Source (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

### Stressor Private by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


### Stressor Private by Care Work

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


### Stressor Private by Residence (national only)

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


# Supervisor


```{r Supervisor, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = "supervisor", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Supervisor by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "supervisor", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Supervisor by Gender

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "supervisor", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

## Supervisor by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "supervisor", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Supervisor by Funding Source (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "supervisor", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Supervisor by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "supervisor", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


## Supervisor by Care Work

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "supervisor", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Supervisor by Residence (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "supervisor", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


# Institution 

```{r Institution, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = "institution", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Institution by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "institution", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Institution by Gender

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "institution", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

## Institution by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "institution", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Institution by Funding Source (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "institution", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Institution by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "institution", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


## Institution by Care Work

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "institution", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Institution by Residence (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "institution", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


# Work-Group

These workgroup-related were answered if they indicated to be in a working group `r round(100*table(dat$workingGroup)/sum(table(dat$workingGroup)),2)[1]`% (n = `r table(dat$workingGroup)[1]`) of the respondents.


```{r Workgroup, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = "workgroup", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Workgroup by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Workgroup by Gender

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

## Workgroup by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Workgroup by Funding Source (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Workgroup by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


## Workgroup by Care Work

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Workgroup by Residence (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


# Discrimination

## Discrimination Experience 

```{r Discrimination, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = "discrimination", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```



## Discrimination Experience by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```



## Discrimination Experience by Gender

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

## Discrimination Experience by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Discrimination Experience by Funding Source (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Discrimination Experience by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


## Discrimination Experience by Care Work

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Discrimination Experience by Residence (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

## Discrimination Dimensions 

```{r Discrimination Dimensions, fig.height= 9, fig.width= 9}

swims.plot.aggregation(var = "discrimination_type", institution = NULL, font_size = multibar.fontSize+2,annoFontSize = multibar.fontSizeInplot)

```

## Discrimination Dimensions by Age? etc.


# Questionable Research Practices

```{r Questionable Reserach Practices, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = "qrp", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Questionable Reserach Practices by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Questionable Reserach Practices by Gender

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

## Questionable Reserach Practices by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Questionable Reserach Practices by Funding Source (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Questionable Reserach Practices by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


## Questionable Reserach Practices by Care Work

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp", divider = "Carework", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Questionable Reserach Practices by Residence (national only)

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

## Pressures to Perform Questionable Reserach Practices 

```{r qrp Dimensions, fig.height= 9, fig.width= 9}

swims.plot.aggregation(var = "qrp_pressure", institution = NULL, font_size = multibar.fontSize+2,annoFontSize = multibar.fontSizeInplot)

```

## Pressures to Perform Questionable Reserach Practices by Age? etc.

## Effects of Pressures to Perform Questionable Reserach Practices on Mental Health


```{r qrp_mh, fig.height= 5 , fig.width= 6}
swims.plot.distribution("pressureqrpMentalhealth")

```


### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Age", annoFontSize = 3)
```

### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Gender", annoFontSize = 3)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Discipline", annoFontSize = 2)
```

### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Funding Source (national only)

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Funding", annoFontSize = 2)
```

### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Position", annoFontSize = 2)
```


### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Care Work

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Carework", annoFontSize = 3)

```


### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Residence (national only)

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Residence", annoFontSize = 3)

```


---
  
# Appendix
  
## Codebook
  
Detailed variable names, item formulations, etc. can be found in the codebook [link]

# References 


