---
title: "National Report: SWiMS 2024 Data"
author: "actionuni Survey Team"
date: "`r Sys.Date()`"
params:
  width_bar: 1
output:
  pdf_document:
    toc: true
    toc_depth: 2
    keep_tex: true
    fig_caption: false
bibliography: references.bib 
classoption: landscape
header-includes:
  - \usepackage{graphicx}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\includegraphics[width=1.5cm]{actionuni_logo_klein.png}}
  - \fancyhead[C]{}
  - \fancyhead[R]{SWiMS 2024 National Report}
  - \usepackage{draftwatermark}
  - \SetWatermarkText{DRAFT}
  - \SetWatermarkScale{1} # Adjust size of watermark
  - \SetWatermarkLightness{0.9} # Adjust transparency (1 = invisible, 0 = solid)
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = FALSE, message = FALSE,
                      fig.width = 9, 
                      fig.height = 5, 
                      out.width = "100%", 
                      dpi = 300)
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(readxl)

# TODO
#width_bar = params$width_bar

```

```{r load-data, include=FALSE}
rm(list = ls())
# Load data
load("../data/SWiMS2024_Data_2025-03-31.RData")
source("zz_utils_helpers.R")
source("zz_utils_distribution.R")
source("zz_utils_aggregation.R")
source("zz_utils_multibar.R")


institution_labels <- strsplit(codebook[codebook$VarName %in% "institution","Labels"],"//")[[1]]

```

# TODOs

- write executive summary
- add new actionuni logo

- demograhpcis -- old gender variable
- new grouping in position type (in codebook)!
- distribution plot by e.g, age, bars width erhöhen damit text lesbar

- aggregation function: do not exclude if there is one NA
- aggregation function: add info if "other" was specified

- codebook cutting of many variables on separate pages
- resources + discReport variable


- für paper: year in phd as important factor!

- @ ZORAN: rename Discrimination Dimensions to "Sources of Discrimination"


# Executive Summary

 \newpage
 
# Introduction


The SWiMS 2024 Survey examines the mental health and well-being of mid-level academic staff across Switzerland, including doctoral researchers, scientific associates, and postdocs. The survey aims to identify key challenges in working conditions and research environments, providing a data-driven foundation for improving policies and support systems at Swiss higher education institutions (HEIs).

This report presents the national-level findings, offering insights into stressors, mental health outcomes, and available resources. By highlighting systemic issues and institutional differences, the data provide a basis for further discussions on how to improve well-being in academia.

## Background and Motivation
Mid-level academic staff are essential to research, teaching, and student supervision, making up approximately 48% of the academic workforce in Switzerland (Federal Statistical Office, 2024). Despite their crucial role, many experience high levels of stress and job insecurity, which can negatively impact both their mental health and the quality of academic work.

Several factors contribute to these challenges, including intense workload, administrative responsibilities, publication pressure, and uncertain career prospects due to the prevalence of temporary contracts. These stressors are well-documented in international research, with studies indicating that 30-40% of early career researchers report mental health issues (Divaris et al., 2012; Gloria & Steinhardt, 2016; Levecque et al., 2017; Evans et al., 2018). Burnout, depression, and anxiety are particularly prevalent, threatening both individual well-being and the sustainability of academic careers (Bolotnyy et al., 2022; Boone et al., 2022; Satinsky et al., 2021).

Despite growing awareness of these issues, Switzerland lacks comprehensive national data on the mental health of mid-level academic staff. While some institutions have conducted internal surveys (e.g., ETH Zurich’s employee survey), a coordinated, nationwide effort has been missing. The reluctance of universities to engage in comparisons—possibly due to reputational concerns—may contribute to this gap. Yet, without broad-based data, it is difficult to develop effective interventions or institution-wide improvements.

## The Swiss-Wide Mental Health Survey (SWiMS)

To address this gap, actionuni, in collaboration with 12 mid-level academic staff associations, launched SWiMS 2024 as a bottom-up initiative. The survey provides the first nationwide assessment of mental health among early career researchers in Switzerland, highlighting both stressors and protective factors.

By systematically analyzing the collected data, the project aims to:

- Expand the knowledge base on mental health in academia.
- Identify key stress factors affecting mid-level academic staff.
- Enable institutions to learn from best practices, improving support systems.
- Provide an evidence-based foundation for discussions on mental health policies.

Ultimately, fostering a healthier academic work environment benefits not only early career researchers but also research quality, institutional innovation, and the broader university system. Ensuring well-being at all career stages is essential for maintaining the long-term excellence and sustainability of Swiss academia.


---
  
 \newpage
 
# Sample Description

## Data cleaning 
Only institutions with more than 10 responses were considered in this report. 43 participants of 16 institution with a mean of 2.7 (SD = 1.81) participants were removed from the dataset. 62 additional responses were removed because institution "Other" (n = 44), "Prefer not to say" (n = 15), or were missing (n = 3) were indicated. We also exculded participants that took shorter than 4 minutes to respond (n = 4). In total, `r nrow(dat)` responses were part of this report.  


## Parttaking institutions and response

```{r, echo = F}

# Calculate the number of participants for each institution
institution_counts <- dat %>%
  group_by(inst) %>%
  summarise(count = n()) %>%
  filter(count > 10)

# Filter the data to include only institutions with more than 20 participants
filtered_dat <- dat %>%
  filter(inst %in% institution_counts$inst)

# Get the maximum count to set y-axis limit
max_count <- max(institution_counts$count)
sum_count <- sum(institution_counts$count)

# Create the plot
ggplot(filtered_dat, aes(x = reorder(factor(inst), table(inst)[factor(inst)]), y = ..count..)) +  
  geom_bar(fill = "steelblue", alpha = 0.7) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    plot.title = element_text(size = 16, hjust = 0.5),
    plot.caption = element_text(size = 8, hjust = 0.5, face = "italic")
  ) +
  labs(
   # title = "Number of Responses by Institution",
    x = "Institution Name",
    y = "Number of Responses",
    caption = paste("Total count: ",sum_count ,"\n",
                    "Only institutions with more than 10 participants are displayed.")
  ) +
  geom_text(stat = 'count', aes(label = ..count..), hjust = -0.1, size = 3.5) +
  ylim(c(0, max_count + 30)) +
  coord_flip()

#ggsave(paste0("../plots/SWiMS_responses_",date ,".pdf"), height = 7, width = 8)
```

The average duration of responding to the survey was `r round(mean(dat[dat$duration < 2*3600,"duration"]/60, na.rm =T),2)` minutes (SD = `r round(sd(dat[dat$duration < 2*3600,"duration"]/60, na.rm =T),2)`).

<!-- ### Response Rate -->

<!-- ```{r} -->

<!-- institution_counts <- institution_counts %>% -->
<!--   left_join(dat.meta %>% select(Name, Members), by = c("inst" = "Name")) # add member numbers -->
<!-- institution_counts$response_rate <- institution_counts$count/institution_counts$Members -->

<!-- # Create the bar chart -->
<!-- ggplot(institution_counts, aes(x = reorder(inst, count))) +  -->
<!--   geom_bar(aes(y = Members), stat = "identity", fill = "lightgray", alpha = 0.7) +  -->
<!--   geom_bar(aes(y = count), stat = "identity", fill = "steelblue", alpha = 0.7) +  -->
<!--   geom_text(aes(y = count, label = sprintf("%.1f%%", response_rate * 100)),  -->
<!--             hjust = -0.1, size = 3.5) + -->
<!--   labs(x = "Institution Name",  -->
<!--        y = "Number of estimated Members (in gray)\n and Responses (in blue)") +  -->
<!--   theme_minimal(base_size = 12) +  -->
<!--   theme( -->
<!--     axis.text.x = element_text(size = 10), -->
<!--     axis.text.y = element_text(size = 10), -->
<!--     axis.title.x = element_text(size = 12), -->
<!--     axis.title.y = element_text(size = 12), -->
<!--     plot.caption = element_text(size = 8, hjust = 0.5, face = "italic") -->
<!--   ) + -->
<!--   coord_flip() + -->
<!--   scale_y_continuous(expand = expansion(mult = c(0, 0.1))) -->

<!-- #ggsave(paste0("../plots/SWiMS_response_rate_",Sys.Date(),".pdf"), height = 7, width = 8) -->

<!-- ``` -->

\newpage

## Demographics 
  
The figures below summarize the key demographic characteristics of all parttaking institutions.

### Age

```{r age, fig.height = 4, fig.width=3}
swims.plot.distribution("age")

```

`r swims.formulation("age")`

For the subsequent analyses this variable was grouped into three categories: "18-30," "31-40," and ">41." Respondents unwilling to disclose their age were coded as missing.






### Gender

```{r gender, fig.height = 4, fig.width=3}
swims.plot.distribution("Gender")
```

`r swims.formulation("female", what = "item")` with answer options "male","female","non-binary", or "prefer not to say".

Recoded from multiple binary selections into categories: "male," "female," or "other" (including nonbinary or multiple selections). 'prefer not to say' responses were coded as missing (NA).

### Research Discipline

```{r , fig.height = 5, fig.width=7}
swims.plot.distribution("researchDiscipline") 

```

`r swims.formulation("researchDiscipline", what = "item")`

Subsequently referred to as "Natural Sciences and Engineering", "Medicine", "Social Sciences", and "Humanities". "Prefer not to say" responses coded as NA.

### Position Type

```{r , fig.height = 4, fig.width=9}
swims.plot.distribution("mainPosition") # + 
    #scale_x_discrete(labels = function(x) str_wrap(x, width = 23))   # Apply text wrapping

```

`r swims.formulation("mainPosition", what = "item")`

Recoded positions into four broad groups: "Researcher aiming for a PhD,", "Postdoctoral researcher", "Other researchers with a PhD", and "Other". "Prefer not to say" responses coded as NA.

### Funding Source

```{r , fig.height = 4, fig.width=7}
swims.plot.distribution("funding")
```
`r swims.formulation("funding", what = "item")`

Original funding categories simplified into three groups: "SNSF", "Non-SNSF funding", and "University/Higher education institute." Ambiguous or undisclosed funding sources coded as missing (NA).

### Residence Status

```{r , fig.height = 4, fig.width=7}
swims.plot.distribution("residenceStatus")
```

`r swims.formulation("residenceStatus", what = "item")`

Subsequently used with residence status reduced to two groups: "Swiss citizenship + Permit C", and "Other Permits." Non-disclosed or unclear responses coded as NA.


#### Employment Status
\

```{r , fig.height =4, fig.width=5}

swims.plot.distribution("employmentStatus")

```

`r swims.formulation("employmentStatus", what = "item")`

\newpage 

### Other Demographic Variables

These variables will not be used for group comparisons later, thus the name "other".


### Care Work

```{r , fig.height = 4, fig.width=3}
swims.plot.distribution("Carework")
```

`r swims.formulation("careKids")`

`r swims.formulation("careFamily")`

Simplified into "care work" (if respondents indicated caring for children/family) or "no care work". Missing or unclear responses were coded as missing.
\newpage

#### Employment Percentage
\

```{r,  fig.height = 4, fig.width=8.5}

swims.plot.distribution("workloadMainjob")

```

`r swims.formulation("workloadMainjob", what = "item")`


\newpage 

#### Additional Non-Academic Job  
\

```{r, fig.height= 4 , fig.width= 4}

swims.plot.distribution("nonacademicJob")

```

`r swims.formulation("nonacademicJob", what = "item")`

\newpage 

# Mental Health

## General Mental Health

`r swims.formulation("mentalHealth", what = "item")`

```{r mental health, fig.height= 4 , fig.width= 5}
swims.plot.distribution("mentalHealth")
```


### General Mental Health by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "mentalHealth", divider = "Age", annoFontSize = 3)
```

### General Mental Health by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "mentalHealth", divider = "Gender", annoFontSize = 3)
```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### General Mental Health by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "mentalHealth", divider = "Discipline", annoFontSize = 2)
```

### General Mental Health by Funding Source

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "mentalHealth", divider = "Funding", annoFontSize = 2)
```

### General Mental Health by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "mentalHealth", divider = "Position", annoFontSize = 2)
```


### General Mental Health by Employment Status

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "mentalHealth", divider = "employmentStatus", annoFontSize = 3)

```


### General Mental Health by Residence

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "mentalHealth", divider = "Residence", annoFontSize = 3)

```


 \newpage
 
## Depression

We computed a depression score by summing the 7 items from the DASS-21 depression subscale. In our sample, this measure showed excellent internal consistency (Cronbach’s alpha = .91), indicating that the items reliably measure the same underlying construct. A total of 62 observations were excluded from this analysis due to missing data on at least one of the depression items.

Following the clinical guidelines proposed by Nilges and Essau [-@nilges_dass_2021], a sum score above 10 is considered indicative of elevated depressive symptoms and may be viewed as clinically relevant.

```{r depression, fig.height= 4 , fig.width= 5}
swims.plot.distribution("Depression")
```

```{r depression2, fig.height= 4 , fig.width= 5}

swims.plot.distribution("DepressionCategory")
```

### Depression by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "DepressionCategory", divider = "Age", annoFontSize = 3)
```

### Depression by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "DepressionCategory", divider = "Gender", annoFontSize = 3)
```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Depression by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "DepressionCategory", divider = "Discipline", annoFontSize = 2)
```

### Depression by Funding Source

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "DepressionCategory", divider = "Funding", annoFontSize = 2)
```

### Depression by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "DepressionCategory", divider = "Position", annoFontSize = 2)
```


### Depression by Employment Status

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "DepressionCategory", divider = "employmentStatus", annoFontSize = 3)

```


### Depression by Residence

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "DepressionCategory", divider = "Residence", annoFontSize = 3)

```

\newpage 


## Burnout


`r swims.formulation("Burnout", what = "item")` 

Item developed by West and colleauges [-@west_single_2009].


```{r burnout, fig.height= 5 , fig.width= 6}
swims.plot.distribution("Burnout")

```


### Burnout by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "Burnout", divider = "Age", annoFontSize = 3)
```

### Burnout by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "Burnout", divider = "Gender", annoFontSize = 3)
```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Burnout by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "Burnout", divider = "Discipline", annoFontSize = 2)
```

### Burnout by Funding Source

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "Burnout", divider = "Funding", annoFontSize = 2)
```

### Burnout by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "Burnout", divider = "Position", annoFontSize = 2)
```


### Burnout by Employment Status

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "Burnout", divider = "employmentStatus", annoFontSize = 3)

```


### Burnout by Residence

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "Burnout", divider = "Residence", annoFontSize = 3)

```

## Awarenes Resources 

```{r awareness resources, fig.height= 5 , fig.width= 6}
swims.plot.multibar("resources")

```

### Awarenes Resources by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.multibar(var = "resources", divider = "Age")
```

### Awarenes Resources by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.multibar(var = "resources", divider = "Gender")
```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Awarenes Resources by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.multibar(var = "resources", divider = "Discipline")
```

### Awarenes Resources by Funding Source

```{r, fig.height= 5, fig.width= 8}
swims.plot.multibar(var = "resources", divider = "Funding")
```

### Awarenes Resources by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.multibar(var = "resources", divider = "Position")
```


### Awarenes Resources by Employment Status

```{r, fig.height= 5, fig.width= 8}
swims.plot.multibar(var = "resources", divider = "employmentStatus")

```


### Awarenes Resources by Residence

```{r, fig.height= 5, fig.width= 7}
swims.plot.multibar(var = "resources", divider = "Residence")

```

 \newpage
 

# Job Satisfaction 

Item formulation: 

*Taking everything into consideration, how satisfied do you feel about your job as a whole?*

Item developed by Dolbier and colleauges [-@dolbier_reliability_2005].


```{r job satisfaction, fig.height= 5 , fig.width= 6}
swims.plot.distribution("jobSatisfaction")

```


### Job Satisfaction  by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "jobSatisfaction", divider = "Age", annoFontSize = 3)
```

### Job Satisfaction  by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "jobSatisfaction", divider = "Gender", annoFontSize = 3)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Job Satisfaction  by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "jobSatisfaction", divider = "Discipline", annoFontSize = 2)
```

### Job Satisfaction  by Funding Source

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "jobSatisfaction", divider = "Funding", annoFontSize = 2)
```

### Job Satisfaction  by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "jobSatisfaction", divider = "Position", annoFontSize = 2)
```


### Job Satisfaction  by Employment Status

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "jobSatisfaction", divider = "employmentStatus", annoFontSize = 3)

```


### Job Satisfaction  by Residence

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "jobSatisfaction", divider = "Residence", annoFontSize = 3)

```


## Quitting Intentions

`r swims.formulation("quitting", what = "item")`

```{r quitting intentions, fig.height= 5 , fig.width= 6}
swims.plot.distribution("quitting")

```


### Quitting Intentions by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "quitting", divider = "Age", annoFontSize = 3)
```

### Quitting Intentions by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "quitting", divider = "Gender", annoFontSize = 3)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Quitting Intentions by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "quitting", divider = "Discipline", annoFontSize = 2)
```

### Quitting Intentions by Funding Source

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "quitting", divider = "Funding", annoFontSize = 2)
```

### Quitting Intentions by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "quitting", divider = "Position", annoFontSize = 2)
```


### Quitting Intentions by Employment Status

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "quitting", divider = "employmentStatus", annoFontSize = 3)

```


### Quitting Intentions by Residence

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "quitting", divider = "Residence", annoFontSize = 3)

```


 \newpage
 

# Stressors

## System

`r swims.formulation("stress", what = "item")`


```{r stress system12, fig.height= 6 , fig.width= 8}

multibar.fontSize = 8
multibar.fontSizeInplot = 2.5

swims.plot.multibar(c("stress_system1","stress_system2","stress_system3"),font_size = multibar.fontSize, rev_colors_set = T)

```

```{r stress system3, fig.height= 6 , fig.width= 8}

swims.plot.multibar(c("stress_system3"),font_size = multibar.fontSize, rev_colors_set = T)

```


### Stressor System by Age


```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system1","stress_system2"), divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system3"), divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor System by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system1","stress_system2"), divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system3"), divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor System by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system1","stress_system2"), divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system3"), divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor System by Funding Source

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system1","stress_system2"), divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system3"), divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor System by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system1","stress_system2"), divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system3"), divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


### Stressor System by Employment Status

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system1","stress_system2"), divider = "employmentStatus", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system3"), divider = "employmentStatus", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

### Stressor System by Residence

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system1","stress_system2"), divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = c("stress_system3"), divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

 \newpage
 
## Stressor Supervisor


`r swims.formulation("stress", what = "item")`



```{r stress supervisor, fig.height= 6 , fig.width= 8}

swims.plot.multibar("stress_supervisor",font_size = multibar.fontSize, rev_colors_set = T)

```


### Stressor Supervisor by Age

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Supervisor by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor Supervisor by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Supervisor by Funding Source

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Supervisor by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


### Stressor Supervisor by Employment Status

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "employmentStatus", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```


### Stressor Supervisor by Residence

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_supervisor", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

 \newpage
 
## Stressor Colleagues


`r swims.formulation("stress", what = "item")`




```{r stress colleagues, fig.height= 6 , fig.width= 8}

swims.plot.multibar("stress_colleagues",font_size = multibar.fontSize, rev_colors_set = T)

```


### Stressor Colleagues by Age

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Colleagues by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor Colleagues by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Colleagues by Funding Source

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Colleagues by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


### Stressor Colleagues by Employment Status

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "employmentStatus", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```


### Stressor Colleagues by Residence

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_colleagues", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

 \newpage
 

## Stressor Self-Management

`r swims.formulation("stress", what = "item")`



```{r stress selfManagement, fig.height= 6 , fig.width= 8}

swims.plot.multibar("stress_selfManagement",font_size = multibar.fontSize, rev_colors_set = T)

```


### Stressor Self-Management by Age

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Self-Management by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor Self-Management by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Self-Management by Funding Source

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Self-Management by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


### Stressor Self-Management by Employment Status

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "employmentStatus", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```


### Stressor Self-Management by Residence

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_selfManagement", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

 \newpage
 

## Stressor Private

`r swims.formulation("stress", what = "item")`


```{r stress private, fig.height= 6 , fig.width= 8}
swims.plot.multibar("stress_private",font_size = multibar.fontSize, rev_colors_set = T)

```


### Stressor Private by Age

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Private by Gender

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```
the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Stressor Private by Research Discipline

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Private by Funding Source

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

### Stressor Private by Position Type

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


### Stressor Private by Employment Status

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "employmentStatus", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```


### Stressor Private by Residence

```{r, fig.height= 6, fig.width= 9}
swims.plot.multibar(var = "stress_private", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

 \newpage
 

# Statements Regarding Supervisor

`r swims.formulation("worklifebalanceSup", what = "item")`

```{r Supervisor1, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = c("supervisor1") , font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot+3)

```

```{r Supervisor2, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = c("supervisor2") , font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot+3)

```

```{r Supervisor3, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = c("supervisor3") , font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot+3)

```


## Supervisor by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor1"), divider = "Age", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor2"), divider = "Age", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor3"), divider = "Age", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```


## Supervisor by Gender


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor1"), divider = "Gender", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)


```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor2"), divider = "Gender", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)


```

the 'other' category entails the non-binary response category or if both male and female gender were indicated


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor3"), divider = "Gender", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

## Supervisor by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor1"), divider = "Discipline", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor2"), divider = "Discipline", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```



```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor3"), divider = "Discipline", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```

## Supervisor by Funding Source

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor1"), divider = "Funding", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor2"), divider = "Funding", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor3"), divider = "Funding", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```


## Supervisor by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor1"), divider = "Position", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor2"), divider = "Position", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor3"), divider = "Position", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```




## Supervisor by Employment Status

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor1"), divider = "employmentStatus", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor2"), divider = "employmentStatus", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor3"), divider = "employmentStatus", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```



## Supervisor by Residence

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor1"), divider = "Residence", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor2"), divider = "Residence", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("supervisor3"), divider = "Residence", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

 \newpage
 

# Statements Regarding Institution 

\normalsize
`r swims.formulation("focusInst", what = "item")`
\normalsize

```{r Institution, fig.height= 8, fig.width= 9}

swims.plot.multibar(var = c("institution1"), font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

```{r Institution2, fig.height= 8, fig.width= 9}

swims.plot.multibar(var = c("institution2"), font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

## Institution by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution1"), divider = "Age", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution2"), divider = "Age", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```

## Institution by Gender

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution1"), divider = "Gender", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution2"), divider = "Gender", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

## Institution by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution1"), divider = "Discipline", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution2"), divider = "Discipline", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```

## Institution by Funding Source

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution1"), divider = "Funding", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution2"), divider = "Funding", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```


## Institution by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution1"), divider = "Position", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution2"), divider = "Position", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)
```



## Institution by Employment Status

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution1"), divider = "employmentStatus", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution2"), divider = "employmentStatus", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```


## Institution by Residence

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution1"), divider = "Residence", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = c("institution2"), divider = "Residence", font_size = multibar.fontSize+4, fontsize_inplot = multibar.fontSizeInplot+2)

```

 \newpage
 
# Statements Regarding Work-Group

These workgroup-related questions were asked only if the respondents indicated to be in a working group, `r round(100*table(dat$workingGroup)/sum(table(dat$workingGroup)),2)[1]`% (n = `r table(dat$workingGroup)[1]`) of the respondents.

`r swims.formulation("collabWorkinggroup", what = "item")`


```{r Workgroup, fig.height= 8, fig.width= 9}

swims.plot.multibar(var = "workgroup", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Workgroup by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Workgroup by Gender

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

## Workgroup by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Workgroup by Funding Source

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```

## Workgroup by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)
```


## Workgroup by Employment Status

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "employmentStatus", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```


## Workgroup by Residence

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "workgroup", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot)

```

 \newpage
 

# Discrimination

## Discrimination Experience 

`r swims.formulation("discriminationWitness", what = "item")`

```{r Discrimination1, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = c("discrimination1"), font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```


```{r Discrimination2, fig.height= 9, fig.width= 9}

swims.plot.multibar(var = c("discrimination2"), font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```



## Discrimination Experience by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination1", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination2", divider = "Age", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```



## Discrimination Experience by Gender

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination1", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination2", divider = "Gender", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated


## Discrimination Experience by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination1", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination2", divider = "Discipline", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

## Discrimination Experience by Funding Source

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination1", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination2", divider = "Funding", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

## Discrimination Experience by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination1", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination2", divider = "Position", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)
```


## Discrimination Experience by Employment Status

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination1", divider = "employmentStatus", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination2", divider = "employmentStatus", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```


## Discrimination Experience by Residence

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination1", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "discrimination2", divider = "Residence", font_size = multibar.fontSize, fontsize_inplot = multibar.fontSizeInplot, rev_colors_set = T)

```



 \newpage
 
## Sources of Dimensions 


`r swims.formulation("discrAge", what = "item")`


```{r Discrimination Dimensions, fig.height= 9, fig.width= 9}

swims.plot.aggregation(var = "discrimination_type", institution_prov = NULL,font_size = multibar.fontSize+4,annoFontSize = multibar.fontSizeInplot)#, annoFontSize = multibar.fontSizeInplot)

```

This plot shows the responses of the subset of respondents (n = `r sum(table(dat$discAge))`; `r sum(table(dat$discAge))/sum(table(dat$discrAge, useNA = "always"))`%), who indicated that they have experienced or witnessed bullying, discrimination, harassment, or other unfair treatment during their position in Switzerland. Each person could name multiple perceived sources of discrimination, resulting in a total of XX responses.


## Amount of Sources of Discrimination
\normalsize
`r swims.formulation("discrAge", what = "item")`
\normalsize
```{r}
swims.plot.aggregation("discrimination_type",
                       font_size = (10 + 5),
                       count_votes_at_all = TRUE)
```



 \newpage
 

# Questionable Research Practices

`r swims.formulation("qrpFalsdata", what = "item")`

```{r Questionable Reserach Practices1, fig.height= 9, fig.width= 9}
qrp.cols <- c("red","#2166AC","gray69","orange","#66C2A5")
swims.plot.multibar(var = "qrp1", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```

```{r Questionable Reserach Practices2, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp2", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```

```{r Questionable Reserach Practices3, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp3", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```


## Questionable Reserach Practices by Age

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp1", divider = "Age", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp2", divider = "Age", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp3", divider = "Age", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```


## Questionable Reserach Practices by Gender

```{r, fig.height= 8.5, fig.width= 9}
swims.plot.multibar(var = "qrp1", divider = "Gender", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```

```{r, fig.height= 8.5, fig.width= 9}
swims.plot.multibar(var = "qrp2", divider = "Gender", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```


the 'other' category entails the non-binary response category or if both male and female gender were indicated

## Questionable Reserach Practices by Research Discipline

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp1", divider = "Discipline", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp2", divider = "Discipline", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp3", divider = "Discipline", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```

## Questionable Reserach Practices by Funding Source

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp1", divider = "Funding", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp2", divider = "Funding", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```


```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp3", divider = "Funding", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```

## Questionable Reserach Practices by Position Type

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp1", divider = "Position", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp2", divider = "Position", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)
```


## Questionable Reserach Practices by Employment Status

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp1", divider = "employmentStatus", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp2", divider = "employmentStatus", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp3", divider = "employmentStatus", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```



## Questionable Reserach Practices by Residence

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp1", divider = "Residence", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp2", divider = "Residence", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```

```{r, fig.height= 9, fig.width= 9}
swims.plot.multibar(var = "qrp3", divider = "Residence", font_size = multibar.fontSize+3, fontsize_inplot = multibar.fontSizeInplot, fill_color_set = qrp.cols)

```


 \newpage
 
## Pressures to Perform Questionable Reserach Practices 

`r swims.formulation("pressureqrpFunder", what = "item")`

```{r qrp Dimensions, fig.height= 5, fig.width= 6}

swims.plot.aggregation(var = "qrp_pressure", institution_prov = NULL, font_size = multibar.fontSize+4,annoFontSize = multibar.fontSizeInplot)


```

 \newpage
 
## Effects of Pressures to Perform Questionable Reserach Practices on Mental Health

`r swims.formulation("pressureqrpMentalhealth", what = "item")`

```{r qrp_mh, fig.height= 5 , fig.width= 6}
swims.plot.distribution("pressureqrpMentalhealth")

```


### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Age

```{r, fig.height= 5, fig.width= 6.5}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Age", annoFontSize = 3)
```

### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Gender

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Gender", annoFontSize = 3)

```

the 'other' category entails the non-binary response category or if both male and female gender were indicated

### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Research Discipline

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Discipline", annoFontSize = 2)
```

### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Funding Source

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Funding", annoFontSize = 2)
```

### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Position Type

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Position", annoFontSize = 2)
```


### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Employment Status

```{r, fig.height= 5, fig.width= 8}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "employmentStatus", annoFontSize = 3)

```


### Effects of Pressures to Perform Questionable Reserach Practices on Mental Health by Residence

```{r, fig.height= 5, fig.width= 7}
swims.plot.distribution(var = "pressureqrpMentalhealth", divider = "Residence", annoFontSize = 3)

```


---
  
  
 \newpage
 
# Appendix
  
## Codebook
  
Detailed variable names, item formulations, etc. can be found in the codebook [link]

# References 


