---
title: "SWiMS 2024 Descriptive Analyses"
author: "TE "
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This survey explores the mental health and well-being of mid-level academic staff (e.g., doctoral researchers, scientific associates, postdocs, and other scientific staff) in Switzerland. The goal of this survey is to identify problems and areas for improvement in working conditions and research environments.

## loading data and R packages

```{r}
library(tidyverse)
library(ggplot2)
rm(list = ls())
load("../data/SWiMS2024_Data_2024-11-14.RData")
```

# Descriptive Analyses

## Responses by Institution

```{r}
# Calculate the number of participants for each institution
institution_counts <- dat %>%
  group_by(institution) %>%
  summarise(count = n()) %>%
  filter(count > 20) %>%
  arrange(count)  # Arrange by count in ascending order

# Filter the data to include only institutions with more than 20 participants
dat <- dat %>%
  filter(institution %in% institution_counts$institution)

# Get the maximum count to set y-axis limit
max_count <- max(institution_counts$count)
sum_count <- sum(institution_counts$count)

# Create the plot
# TODO: Order by response count
ggplot(dat, aes(x = reorder(factor(institution), table(institution)[factor(institution)]), y = after_stat(count))) +  
  geom_bar(fill = "steelblue", alpha = 0.7) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.caption = element_text(size = 8, hjust = 0.5, face = "italic")
  ) +
  labs(
    x = "Institution Name",
    y = "Number of Responses",
    caption = paste("Date:", Sys.Date(), "\n", "Total count: ", sum_count, "\n",
                    "Only institutions with more than 20 participants are displayed.")
  ) +
  geom_text(stat = 'count', aes(label = after_stat(count)), hjust = -0.1, size = 3.5) +
  ylim(c(0, max_count + 30)) +
  coord_flip()  # Flip the coordinates for a horizontal bar chart


#ggsave(paste0("../plots/SWiMS_responses_",Sys.Date(),".pdf"), height = 7, width = 8)
```

## Responses by Date

```{r, fig.width= 10}
# plot responses by date
# Count the number of responses per date
response_counts <- dat %>%
  group_by(date, institution) %>%
  summarise(count = n())

# Create the plot
ggplot(response_counts, aes(x = date, y = count, fill = factor(institution))) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Number of Responses by Date",
       x = "Date",
       y = "Number of Responses") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

```

## Duration 
```{r}
ggplot(dat[dat$duration/3600 < 2,], aes(x = duration/3600)) +
  geom_histogram() +
  xlab("duration in h")
```


-1 means that the participant interrupted the survey and later completed it. For these participant the value of the dispcode value is "Beendet nach Unterbrechung (32)". 

```{r}
##Number of people with the value -1 in the variable duration
# Count the number of participants with a duration of -1
num_negative_duration <- sum(dat$duration == -1, na.rm = TRUE)

# Print the result
print(paste("Number of participants with a duration of -1:", num_negative_duration))

##Plot of duration in min
ggplot(dat[dat$duration/60 < 30,], aes(x = duration/60)) +
  geom_histogram() +
  xlab("duration in min")
```

TODO: Compute average duration and SD for those who used less than 1 h.
```{r}
# Filter data for participants who used less than 1 hour (3600 seconds)
under_1h <- dat[dat$duration < 3600, ]

# Calculate the mean and standard deviation in minutes
average_duration <- mean(under_1h$duration / 60, na.rm = TRUE)
sd_duration <- sd(under_1h$duration / 60, na.rm = TRUE)

# Print the results in minutes
print(paste("Average duration for participants who used less than 1 hour:", round(average_duration, 2), "minutes"))
print(paste("Standard deviation of duration for participants who used less than 1 hour:", round(sd_duration, 2), "minutes"))

```

TODO:Compute depression score based on Brown et al. 1997 as a new variable depression --> using the short version of the DASS-21 with the depression subscale consisting of 7 items. Scoring: add scores and x2 to get comparable measures as the DASS-42 questionnaire(Henry & Crawford, 2005)
```{r}

# List of the variables
variables <- c("positiveFeeling", "initiative", "future", 
               "feelingDown", "enthusiasm", "selfworth", "meaning")

# Modify the dat data frame in place by mapping categorical responses to numerical scale
dat <- dat %>%
  mutate(across(all_of(variables), ~ recode(.,
    "Did not apply to me at all" = 0,
    "Applied to me to some degree, or some of the time" = 1,
    "Applied to me to a considerable degree, or a good part of time" = 2,
    "Applied to me very much, or most of the time" = 3
  )))


# Create the new variable 'depression' by summing up the specified columns and multiplying by 2 (due to short version)
dat <- dat %>%
  mutate(depression = rowSums(select(., all_of(variables)), na.rm = TRUE) * 2)

# Display the updated data frame with the new 'depression' variable
#dat$depression
psych::describe(dat$depression)

```


TODO: Compare values of existing questionnaires in the survey with averages in the general population and if there is data on this also of other academics (see job satisfaction item by Dolbier et al., 2005, stress item by [Elo et al., 2003] depression items by [Brown et al., 1997] and burnout item by [West et al., 2009], see references below for details)

```{r}
###job satisfaction --> I did not find a population score with that exact item expect for the original study

## Population mean and SD from Dolbier et al. (2005) from 745 workers at the Texas Department of Human Services.
population_mean_js <- 5.31
population_sd_js <- 1.21

# Modify the dat data frame in place by mapping categorical responses to numerical scale --> 0 (skipped question) were converted to NA
dat <- dat %>%
  mutate(jobSatisfaction = case_when(
    jobSatisfaction == "0" ~ NA_character_,
    jobSatisfaction == "1 - extremely dissatisfied" ~ "1",
    jobSatisfaction == "2" ~ "2",
    jobSatisfaction == "3" ~ "3",
    jobSatisfaction == "4" ~ "4",
    jobSatisfaction == "5" ~ "5",
    jobSatisfaction == "6" ~ "6",
    jobSatisfaction == "7 - extremely satisfied" ~ "7",
    TRUE ~ jobSatisfaction
  )) %>% mutate(jobSatisfaction = as.numeric(jobSatisfaction))


# Calculate mean and SD for job satisfaction in your data
survey_mean_js <- mean(dat$jobSatisfaction, na.rm = TRUE)
survey_sd_js <- sd(dat$jobSatisfaction, na.rm = TRUE)

# Perform a t-test to compare the survey data with the population mean
t_test_result <- t.test(dat$jobSatisfaction, mu = population_mean_js)
t_test_result

# Display t-test result in a table with sjPlot
sjPlot::tab_df(
  data.frame(
    Group = c("Survey", "Population"),
    Mean = c(survey_mean_js, population_mean_js),
    SD = c(survey_sd_js, population_sd_js),
    "t-test" = t_test_result$statistic,
    "df" = t_test_result$parameter,
    "t-test p-value" = t_test_result$p.value
  ),
  title = "Descriptive Statistics and T-test Result"
)

```

## Stress

Elo, A. L., Leppänen, A., & Jahkola, A. (2003). Validity of a single-item measure of stress symptoms. Scandinavian journal of work, environment & health, 444-451.

```{r}
##Stress

# Modify the dat data frame in place by mapping categorical responses to numerical scale --> 0 (skipped question) were converted to NA
dat <- dat %>%
  mutate(stress = recode(as.character(stress),
    "1 - not at all" = 1,
    "2" = 2,
    "3" = 3,
    "4" = 4,
    "5 - very much" = 5
  ))

# Check data
#dat$stress
summary(dat$stress)

# Calculate mean and SD for job satisfaction 
survey_mean_stress <- mean(dat$stress, na.rm = TRUE)
survey_sd_stress <- sd(dat$stress, na.rm = TRUE)

# Natalie Pennington, Amanda J. Holmstrom & Jeffrey A. Hall (2022) The Toll
# of Technology while Working from Home during COVID-19, Communication Reports, 35:1,
# 25-37, DOI: 10.1080/08934215.2021.1993947
#we commissioned the Siena College Research Institute (SCRI) and the panel company, Lucid, to survey American adults in May 2020. Participants were recruited to establish a quota sample of age, sex, political affiliation, region of the country, and race and ethnicity. 
jeff_M = 2.89
jeff_SD = 1.22
#N = 540


# Perform a t-test to compare the survey data with the population mean
#t_test_result <- t.test(survey_mean_stress, mu = jeff_M)
# #t_test_result
# 
# # Display t-test result in a table with sjPlot
# sjPlot::tab_df(
#   data.frame(
#     Group = c("Survey", "Population"),
#     Mean = c(survey_mean_stress, jeff_M),
#     SD = c(survey_sd_stress, jeff_SD),
#     "t-test" = t_test_result$statistic,
#     "df" = t_test_result$parameter,
#     "t-test p-value" = t_test_result$p.value
#   ),
#   title = "Descriptive Statistics and T-test Result"
# )


#more numbers from: Elo, A. L., Ervasti, J., Kuosma, E., & Mattila, P. (2008). Evaluation of an organizational stress management program in a municipal public works organization. Journal of occupational health psychology, 13(1), 10–23. https://doi.org/10.1037/1076-8998.13.1.10
mean_pre <- 2.30
sd_pre <- 1.10
n = 218



#Arapovic-Johansson, B., Wåhlin, C., Kwak, L., Björklund, C., & Jensen, I. (2017). Work-related stress assessed by a text message single-item stress question. Occupational medicine (Oxford, England), 67(8), 601–608. https://doi.org/10.1093/occmed/kqx111 --> is with SMS and only median.

# N = 118, Participants were employed at three team-based primary health care facilities, so not really represantive

# ## Population median and SD from Arapovic-Johansson (2017)
# population_median_stress <- 3
# 
# # Perform a Wilcoxon signed-rank test to compare the sample median with the population median
# wilcox_test_result_stress <- wilcox.test(dat$stress, mu = population_median_stress, exact = FALSE)
# 
# # Display Wilcoxon test result in a table with sjPlot
# sjPlot::tab_df(
#   data.frame(
#     Group = c("Survey", "Population"),
#     Median = c(survey_median_stress, population_median_stress),
#     "Wilcoxon test" = wilcox_test_result_stress$statistic,
#     "Wilcoxon p-value" = wilcox_test_result_stress$p.value
#   ),
#   title = "Descriptive Statistics and Wilcoxon Test Result"
# )

```


## Burnout

West, C. P., Dyrbye, L. N., Sloan, J. A., & Shanafelt, T. D. (2009). Single item measures of emotional exhaustion and depersonalization are useful for assessing burnout in medical professionals. Journal of general internal medicine, 24(12), 1318–1321. https://doi.org/10.1007/s11606-009-1129-z 

Emotional exhaustion item

```{r}
##Burnout --> scale 0-6

unique(dat$burnOut)

# Modify the dat data frame in place by mapping categorical responses to numerical scale --> 0 (skipped question) were converted to NA
dat <- dat %>%
  mutate(burnOut = recode(as.character(burnOut),
    "Never" = 0,
    "A few times a year or less" = 1,
    "Once a month or less" = 2,
    "A few times a month" = 3,
    "Once a week" = 4,
    "A few times a week" = 5,
    "Everyday" = 6
  ))

hist(dat$burnOut)

```


## Depression 

```{r}
###Depression --> no papers found specifically about academia

##comparison paper: Henry, J., & Crawford, J. (2005). The short-form version of the Depression Anxiety Stress Scales (DASS-21): construct validity and normative data in a large non-clinical sample. The British journal of clinical psychology, 44 Pt 2, 227-39 . https://doi.org/10.1348/014466505X29657.

#participants: 1,794 members of the general adult UKpopulation non clinical (979 female, 815 male)

# Given mean and standard deviation from the comparison paper
comparison_mean_depr1 <- 3.87
comparison_sd_depr1 <- 0.83  

# Calculate the mean and standard deviation for your survey's depression variable
survey_mean_depr <- mean(dat$depression, na.rm = TRUE)
survey_sd_depr <- sd(dat$depression, na.rm = TRUE)

# Perform a t-test to compare the survey data with the population mean
t_test_result_depr <- t.test(dat$depression, mu = comparison_mean_depr1)
t_test_result_depr

# Display t-test result in a table with sjPlot
sjPlot::tab_df(
  data.frame(
    Group = c("Survey", "Population"),
    Mean = c(survey_mean_depr, comparison_mean_depr1),
    SD = c(survey_sd_depr, comparison_sd_depr1),
    "t-test" = t_test_result_depr$statistic,
    "df" = t_test_result_depr$parameter,
    "t-test p-value" = t_test_result_depr$p.value
  ),
  title = "Descriptive Statistics and T-test Result"
)

##comparison paper: Sinclair, S. J., Siefert, C. J., Slavin-Mulford, J. M., Stein, M. B., Renna, M., & Blais, M. A. (2012). Psychometric evaluation and normative data for the depression, anxiety, and stress scales-21 (DASS-21) in a nonclinical sample of U.S. adults. Evaluation & the health professions, 35(3), 259–279. https://doi.org/10.1177/0163278711424282

#partipants: N = 499 non-clinical sample of US adults

# Given mean and standard deviation from the comparison paper
comparison_mean_depr2 <- 5.70
comparison_sd_depr2 <- 8.20

# Perform a t-test to compare the survey data with the population mean
t_test_result_depr2 <- t.test(dat$depression, mu = comparison_mean_depr2)
t_test_result_depr2

# Display t-test result in a table with sjPlot
sjPlot::tab_df(
  data.frame(
    Group = c("Survey", "Population"),
    Mean = c(survey_mean_depr, comparison_mean_depr2),
    SD = c(survey_sd_depr, comparison_sd_depr2),
    "t-test" = t_test_result_depr2$statistic,
    "df" = t_test_result_depr2$parameter,
    "t-test p-value" = t_test_result_depr2$p.value
  ),
  title = "Descriptive Statistics and T-test Result"
)

```

```{r}
# Create an empty list to store each summary
summary_list <- list()

# Function to create a summary dataframe for tab_df and add it to the summary list
create_summary <- function(group, mean, sd, t_stat, df, p_value, title, reference) {
  summary_list <<- append(summary_list, list(
    data.frame(
      Group = group,
      Mean = mean,
      SD = sd,
      `t-test` = t_stat,
      `df` = df,
      `t-test p-value` = p_value,
      Title = title,
      Reference = reference
    )
  ))
}

# Summary for Job Satisfaction
create_summary(
  group = c("SWiMS Survey", "Population"),
  mean = c(survey_mean_js, population_mean_js),
  sd = c(survey_sd_js, population_sd_js),
  t_stat = t_test_result$statistic,
  df = t_test_result$parameter,
  p_value = t_test_result$p.value,
  title = "Job Satisfaction",
  reference = "Dolbier et al., 2005"
)

# Summary for Stress
create_summary(
  group = c("SWiMS Survey", "Population"),
  mean = c(survey_mean_stress, jeff_M),
  sd = c(survey_sd_stress, jeff_SD),
  t_stat = t_test_result$statistic,
  df = t_test_result$parameter,
  p_value = t_test_result$p.value,
  title = "Stress",
  reference = "Pennington et al., 2022"
)

# Summary for Depression (using comparison from Henry & Crawford, 2005)
create_summary(
  group = c("SWiMS Survey", "Population"),
  mean = c(survey_mean_depr, comparison_mean_depr1),
  sd = c(survey_sd_depr, comparison_sd_depr1),
  t_stat = t_test_result_depr$statistic,
  df = t_test_result_depr$parameter,
  p_value = t_test_result_depr$p.value,
  title = "Depression",
  reference = "Henry & Crawford, 2005"
)

# Summary for Depression (using comparison from Sinclair et al., 2012)
create_summary(
  group = c("SWiMS Survey", "Population"),
  mean = c(survey_mean_depr, comparison_mean_depr2),
  sd = c(survey_sd_depr, comparison_sd_depr2),
  t_stat = t_test_result_depr2$statistic,
  df = t_test_result_depr2$parameter,
  p_value = t_test_result_depr2$p.value,
  title = "Depression",
  reference = "Sinclair et al., 2012"
)

# Combine all summaries into a single data frame
combined_summary <- do.call(rbind, summary_list)

# Display the combined summary using sjPlot::tab_df
sjPlot::tab_df(
  combined_summary,
  title = "Summary of Descriptive Statistics and T-test Results for All Analyses"
)

```

# References 

Brown, T. A., Chorpita, B. F., Korotitsch, W., & Barlow, D. H. (1997). Psychometric properties of the Depression Anxiety Stress Scales (DASS) in clinical samples. Behaviour research and therapy, 35(1), 79-89.

Dolbier, C. L., Webster, J. A., McCalister, K. T., Mallon, M. W., & Steinhardt, M. A. (2005). Reliability and validity of a single-item measure of job satisfaction. American journal of health promotion : AJHP, 19(3), 194–198. https://doi.org/10.4278/0890-1171-19.3.194

Elo, A. L., Leppänen, A., & Jahkola, A. (2003). Validity of a single-item measure of stress symptoms. Scandinavian journal of work, environment & health, 444-451.
West, C. P., Dyrbye, L. N., Sloan, J. A., & Shanafelt, T. D. (2009). Single item measures of emotional exhaustion and depersonalization are useful for assessing burnout in medical professionals. Journal of general internal medicine, 24(12), 1318–1321. https://doi.org/10.1007/s11606-009-1129-z 

Elo, A. L., Ervasti, J., Kuosma, E., & Mattila, P. (2008). Evaluation of an organizational stress management program in a municipal public works organization. Journal of occupational health psychology, 13(1), 10–23. https://doi.org/10.1037/1076-8998.13.1.10

Henry, J., & Crawford, J. (2005). The short-form version of the Depression Anxiety Stress Scales (DASS-21): construct validity and normative data in a large non-clinical sample. The British journal of clinical psychology, 44 Pt 2, 227-39 . https://doi.org/10.1348/014466505X29657.

Natalie Pennington, Amanda J. Holmstrom & Jeffrey A. Hall (2022) The Toll of Technology while Working from Home during COVID-19, Communication Reports, 35:1,
25-37, DOI: 10.1080/08934215.2021.1993947

Sinclair, S. J., Siefert, C. J., Slavin-Mulford, J. M., Stein, M. B., Renna, M., & Blais, M. A. (2012). Psychometric evaluation and normative data for the depression, anxiety, and stress scales-21 (DASS-21) in a nonclinical sample of U.S. adults. Evaluation & the health professions, 35(3), 259–279. https://doi.org/10.1177/0163278711424282

